### 2012-11-15 proposal/proposal.tex
Create initial LaTeX structure for proposal

% proposal.tex | CS 6260 - "Vendetta" Proposal

% setup
\documentclass[9pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fullpage}
\usepackage{color}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{array}
\usepackage{minted}
\usepackage{graphicx}
\usepackage{parskip}

% don't number sections
\setcounter{secnumdepth}{0}

% don't highlight links
\hypersetup{hidelinks}

% custom commands
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:} \emph{#1}}}
\newcommand{\term}[1]{\textit{#1}}
\newcommand{\bterm}[1]{\textbf{\textit{#1}}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\super}[1]{\textsuperscript{#1}}
\newcommand{\sub}[1]{\textsubscript{#1}}

% title
\title{``Vendetta'': End-to-end auditable voting}
\date{}
\author{Kelsey Francis, Curtis Free, Christopher Martin}

% document
\begin{document}
	\maketitle

	\todo{Write the proposal.}
	\cite{dummy}

	\bibliography{sources}{}
	\bibliographystyle{plain}
\end{document}

% vim: set colorcolumn=101 cursorcolumn cursorline:

### 2012-11-15 proposal/proposal.tex
First draft of the proposal
Added a first draft that certainly warrants additional work. Little
research has been performed (on my part) at this point, so it's more of
a "statement of objectives" -- nearly what we discussed in-person.

So, I think the next step is research. Can we clarify the goals we
believe a system should meet? We also need to find "real" references
(not Wikipedia). Finally, we need to clarify what we're going to do, as
I don't think I accurately captured it in what I have written at
present.

@@
 
-	\todo{Write the proposal.}
-	\cite{dummy}
+	\section{Background}
+
+		A democratic voting system like that in the United States raises several questions to which
+		cryptography can potentially provide answers. Namely, the question at hand is \emph{how to keep
+		voting fair}. In particular, we want to consider the following questions:
+		\begin{itemize}
+
+			\item
+				How can a government prove to a voter that his/her vote \emph{was} counted (correctly),
+				without being able to reveal the candidate for which the ballot was cast?
+
+			\item
+				How can an observer verify that the votes reported by a state contain no forged votes (i.e.,
+				that the state is not cheating by introducing votes not actually cast)?
+
+		\end{itemize}
+		Cryptographic systems designed to meet exactly these goals are called \term{end-to-end auditable
+		voting systems}\cite{end_to_end}.
+
+		A wealth of research has been done in this area, and a number of such systems have been devised.
+		Most of these systems have been developed by academia. However, countries such as Estonia and
+		even the United States have developed systems for voting via the Internet
+		\cite{estonia,us_vs_est} -- and while that is only tangential to the questions posed above, it
+		can be instructive to see how (if at all) these systems meet those goals.
+
+	\section{Proposal}
+
+		We plan to begin with a more precise quantification of the security goals that we believe must
+		be met for a voting system (whether physical or digital) in order to accomplish the higher-level
+		goals questioned above. We will then survey existing research on such cryptographic systems to
+		determine whether any fully meet the security requirements.
+
+		Should an existing system sufficiently meet our requirements, we plan to construct a
+		proof-of-concept implementation of the system along with an analysis both of its effectiveness
+		at ensuring fairness and of the feasibility of employing such a system in the real world.
+
+		Otherwise, we will examine the flaws and strengths of the existing designs and attempt to
+		construct a sufficient system -- or in the least, one that shows a marked improvement over
+		prior work. We will then provide an analysis of how our proposed \emph{new} system meets the
+		stated goals and could prove useful in a real-world deployment. Time permitting, we will also
+		implement a proof-of-concept for our scheme.
 

### 2012-11-16 proposal/proposal.tex
Display content in two columns
Suggested by Chris.
Shell escape isn't necessary
Add one-column abstract
Suggested by Chris.
Write abstract for the proposal

@@
 % setup
-\documentclass[9pt]{article}
+\documentclass[10pt]{article}
 \usepackage{amsmath}
@@
 \usepackage{array}
-\usepackage{minted}
 \usepackage{graphicx}
 \usepackage{parskip}
+\usepackage{multicol}
 
@@
 % title
-\title{``Vendetta'': End-to-end auditable voting}
+\title{Cryptographic techniques to ensure fair elections}
 \date{}
@@
 	\maketitle
+
+	\begin{abstract}
+		Traditional election processes are generally accepted by voters though they do not necessarily
+		\emph{prove} to participants that the vote counting was fair. Researchers have developed
+		mechanisms to replace or accompany these existing processes that \emph{do} provide such
+		guarantees through use of cryptography, which allows some degree of ``fairness'' to be proven
+		while keeping ballots secret. For this project, we will attempt to quantify what security goals
+		must be met in order to consider an election ``fair,'' survey existing literature on the matter,
+		and -- time permitting -- produce a proof-of-concept implementation of what we find to be the
+		``best'' system or of our own that uses borrowed techniques in an attempt to meet all necessary
+		goals.
+	\end{abstract}
+
+	\begin{multicols}{2}
 
@@
 
+	\end{multicols}
+
 	\bibliography{sources}{}

### 2012-11-16 proposal/proposal.tex
Clean up the proposal body

--- 2012-11-15 proposal/proposal.tex
@@
 
-	\todo{Write the proposal.}
-	\cite{dummy}
+	\begin{abstract}
+		Traditional election processes are generally accepted by voters though they do not necessarily
+		\emph{prove} to participants that the vote counting was fair. Researchers have developed
+		mechanisms to replace or accompany these existing processes that \emph{do} provide such
+		guarantees through use of cryptography, which allows some degree of ``fairness'' to be proven
+		while keeping ballots secret. For this project, we will attempt to quantify what security goals
+		must be met in order to consider an election ``fair,'' survey existing literature on the matter,
+		and -- time permitting -- produce a proof-of-concept implementation of what we find to be the
+		``best'' system or of our own that uses borrowed techniques in an attempt to meet all necessary
+		goals.
+	\end{abstract}
+
+	\begin{multicols}{2}
+
+		\section{Background}
+
+			Fairness of elections is of vital importance to nations such as the United States in which
+			government officials are elected to office by the people.
+
+			But how often is this fairness challenged? Given voting systems widely used today, citizens
+			must trust that the government (a) counts all cast votes (correctly) and (b) counts
+			\emph{only} votes actually cast.
+
+			Researchers have proposed a variety of systems that make use of cryptography to empower the
+			people to verify in an election that one or both of those requirements has been met by the
+			body performing the election -- with the crucial stipulation that this verification allows
+			individual ballots to remain secret.
+
+		\section{Proposal}
+
+			Our project will accomplish three goals.
+
+			\subsection{Specification of security goals}
+
+				We plan to begin by defining what requirements we believe must be met in order for an
+				election to be considered ``fair'' and translating those requirements into precise security
+				goals that we can reason about using cryptographic techniques. (For example, at what points
+				in the election should we require authenticated encryption, and what are the appropriate
+				unforgeability constraints?)
+
+			\subsection{Literature survey}
+
+				We will then study existing literature on the subject, paying close attention to existing
+				end-to-end auditable voting systems, including both in-person systems (our primary focus)
+				such as Scantegrity \cite{scantegrity} and Pr\^{e}t \`{a} Voter \cite{preta} and online
+				voting systems that attempt to meet the same goals such as Helios \cite{helios}.
+
+			\subsection{Proof-of-concept implementation}
+
+				Having surveyed prior research, and time-permitting, we will consider the extent to which
+				previously-developed systems meet our requirements and construct a proof-of-concept
+				implementation of one such system or one of our own design, using borrowed techniques in
+				an attempt to meet all the goals we set forth.
 
@@
 		\bibliographystyle{plain}
+
+	\end{multicols}
+
 \end{document}

### 2012-11-16 proposal/proposal.tex
Add email addresses
Rephrase abstract text

@@
 \date{}
-\author{Kelsey Francis, Curtis Free, Christopher Martin}
+\author{
+\begin{tabular}{c c c}
+Kelsey Francis & Curtis Free & Christopher Martin \\
+\small \tt{francis@gatech.edu} & \small \tt{curtis.free@gatech.edu} & \small \tt{chris.martin@gatech.edu}
+\end{tabular}
+}
 
@@
 	\begin{abstract}
-		Traditional election processes are generally accepted by voters though they do not necessarily
-		\emph{prove} to participants that the vote counting was fair. Researchers have developed
-		mechanisms to replace or accompany these existing processes that \emph{do} provide such
-		guarantees through use of cryptography, which allows some degree of ``fairness'' to be proven
-		while keeping ballots secret. For this project, we will attempt to quantify what security goals
-		must be met in order to consider an election ``fair,'' survey existing literature on the matter,
-		and -- time permitting -- produce a proof-of-concept implementation of what we find to be the
-		``best'' system or of our own that uses borrowed techniques in an attempt to meet all necessary
-		goals.
+		Current election processes do not allow participants to verify the accuracy of vote counting.
+		Applied cryptography research has yielded a number of candidate systems to replace or accompany
+		voting existing voting procedures to provide fairness guarantees while maintaining ballot secrecy.
+		We will define a set of security properties sufficient to make an election both ``fair'' and ``secret'',
+		survey existing literature on the matter, and -- if time permits -- produce a proof-of-concept
+		implementation of a system that meets these goals (either the best system we find, or one of
+		our own creation using borrowed techniques).
 	\end{abstract}
-
 	\begin{multicols}{2}

### 2012-11-16 proposal/proposal.tex
Rewrite things, kill the mostly-redundant abstract

@@
 \documentclass[10pt]{article}
-\usepackage{amsmath}
-\usepackage{amssymb}
 \usepackage{fullpage}
-\usepackage{color}
 \usepackage{enumerate}
 \usepackage{hyperref}
-\usepackage{mathtools}
-\usepackage{listings}
-\usepackage{array}
-\usepackage{graphicx}
-\usepackage{parskip}
 \usepackage{multicol}
@@
 % title
-\title{Cryptographic techniques to ensure fair elections}
+\title{Cryptographic assurance of fairness in voting}
 \date{}
@@
 
-	\begin{abstract}
-		Current election processes do not allow participants to verify the accuracy of vote counting.
-		Applied cryptography research has yielded a number of candidate systems to replace or accompany
-		voting existing voting procedures to provide fairness guarantees while maintaining ballot secrecy.
-		We will define a set of security properties sufficient to make an election both ``fair'' and ``secret'',
-		survey existing literature on the matter, and -- if time permits -- produce a proof-of-concept
-		implementation of a system that meets these goals (either the best system we find, or one of
-		our own creation using borrowed techniques).
-	\end{abstract}
+\thispagestyle{empty}
+
 \begin{multicols}{2}
@@
 
-			Fairness of elections is of vital importance to nations such as the United States in which
-			government officials are elected to office by the people.
+Citizens' ability to trust the fairness of elections is vital to governments whose rule
+is subject to the consent of the governed, but it is not uncommon for the veracity of
+election results to come into question.
+Current election processes do not allow participants to verify the accuracy of vote counting.
 
-			But how often is this fairness challenged? Given voting systems widely used today, citizens
-			must trust that the government (a) counts all cast votes (correctly) and (b) counts
-			\emph{only} votes actually cast.
+Problems such as identity fraud and equality of ballot access are not amenable to
+cryptographic solutions, but their propensity to be externally observable limits the
+potential for widespread abuse.
+Internal manipulation by the government conducting the poll is a more insidious threat,
+and it is here where we may fruitfully apply cryptography to ensure honesty.
+Research in this field has yielded a number of candidate systems to replace or accompany
+existing voting procedures to provide fairness guarantees while maintaining ballot secrecy.
 
-			Researchers have proposed a variety of systems that make use of cryptography to empower the
-			people to verify in an election that one or both of those requirements has been met by the
-			body performing the election -- with the crucial stipulation that this verification allows
-			individual ballots to remain secret.
+% But how often is this fairness challenged? Given voting systems widely used today, citizens
+% must trust that the government (a) counts all cast votes (correctly) and (b) counts
+% \emph{only} votes actually cast.
 
-		\section{Proposal}
+% Researchers have proposed a variety of systems that make use of cryptography to empower the
+% people to verify in an election that one or both of those requirements has been met by the
+% body performing the election -- with the crucial stipulation that this verification allows
+% individual ballots to remain secret.
 
-			Our project will accomplish three goals.
+\section{Security goals}
 
-			\subsection{Specification of security goals}
+We will formulate a precise security definitions of requirements we believe
+must be met  in a ``fair'' and ``private'' election.
 
-				We plan to begin by defining what requirements we believe must be met in order for an
-				election to be considered ``fair'' and translating those requirements into precise security
-				goals that we can reason about using cryptographic techniques. (For example, at what points
-				in the election should we require authenticated encryption, and what are the appropriate
-				unforgeability constraints?)
+Fairness requires that enough information is published such that anyone is able to
+independently tabulate results, and a receipt given to each voter provides evidence
+of fraud in the event that the voter's ballot is miscounted.
 
-			\subsection{Literature survey}
+Ballot secrecy is a constraint that most cryptography applications do not require.
+When votes are counted correctly, a voter must not be able to prove any
+facts about the ballot that was cast.
+
+\section{Literature survey}
 
 We will then study existing literature on the subject, paying close attention to existing
-				end-to-end auditable voting systems, including both in-person systems (our primary focus)
-				such as Scantegrity \cite{scantegrity} and Pr\^{e}t \`{a} Voter \cite{preta} and online
-				voting systems that attempt to meet the same goals such as Helios \cite{helios}.
+end-to-end auditable voting systems.
+Our primary focus is in-person systems such as Scantegrity \cite{scantegrity} and
+Pr\^{e}t \`{a} Voter \cite{preta}.
+We also consider online voting systems such as Helios \cite{helios}.
 
-			\subsection{Proof-of-concept implementation}
+\section{Proof of concept}
 
-				Having surveyed prior research, and time-permitting, we will consider the extent to which
-				previously-developed systems meet our requirements and construct a proof-of-concept
-				implementation of one such system or one of our own design, using borrowed techniques in
-				an attempt to meet all the goals we set forth.
+If time permits, we will construct a proof-of-concept implementation of a system that meets
+our goals, based on the systems described in the literature if they are sufficient.
 
@@
 \end{document}
-
-% vim: set colorcolumn=101 cursorcolumn cursorline:

### 2012-12-04 paper/paper.tex
Initial work on paper

% paper.tex | CS 6260 - "Vendetta" Paper

% setup
\documentclass[10pt]{article}
\usepackage{color}
\usepackage{enumerate}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{multicol}

% don't number sections
\setcounter{secnumdepth}{0}

% don't highlight links
\hypersetup{hidelinks}

% custom commands
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:} \emph{#1}}}
\newcommand{\term}[1]{\textit{#1}}
\newcommand{\bterm}[1]{\textbf{\textit{#1}}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\super}[1]{\textsuperscript{#1}}
\newcommand{\sub}[1]{\textsubscript{#1}}

% title
\title{Cryptographic assurance of fairness in voting}
\date{}
\author{
\begin{tabular}{c c c}
Kelsey Francis & Curtis Free & Christopher Martin \\
\small \tt{francis@gatech.edu} & \small \tt{curtis.free@gatech.edu} & \small \tt{chris.martin@gatech.edu}
\end{tabular}
}

% document
\begin{document}
\maketitle

\thispagestyle{empty}

\begin{abstract}

  Current election processes do not allow participants to verify the accuracy of vote counting.
  Applied cryptography research has yielded a number of candidate systems to replace or accompany
  existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
	how three popular verifable voting systems -- Scantegrity, Pr\^{e}t \`{a} Voter, and Helios --
	use cryptographic techniques to meet those goals.

\end{abstract}

\begin{multicols}{2}

\section{Introduction}

Citizens' ability to trust the fairness of elections is vital to governments whose rule is subject
to the consent of the governed, but it is not uncommon for the veracity of election results to come
into question.  Current election processes do not allow participants to verify the accuracy of vote
counting.

Problems such as identity fraud and equality of ballot access are not amenable to cryptographic
solutions, but their propensity to be externally observable limits the potential for widespread
abuse.  Internal manipulation by the government conducting the poll is a more insidious threat, and
it is here where we may fruitfully apply cryptography to ensure honesty. Research in this field has
yielded a number of candidate systems to replace or accompany existing voting procedures to provide
fairness guarantees while maintaining ballot secrecy.

In this survey, we will study three of the most well-known solutions: the in-person voting systems
Scantegrity and Pr\^{e}t \`{a} Voter and the online voting system Helios.

First, we will discuss the background of verifiable voting schemes and the security goals they
strive to satisfy. Second, we will describe each of the three voting schemes in turn. We will then
analyze their differing approaches to security and how well they meet the necessary goals. Finally,
we will present some ideas that are not -- but perhaps should be -- considered by these schemes, and
we will draw conclusions about the role of these schemes in elections today and in the future.

\section{Background}

A ``verifiable'' election is one in which the voters may rest assured that the body holding the
election (e.g., a government) reports final vote tallies that exactly reflect votes as they were
cast by the electorate.

\subsection{Ballot secrecy}

In many ways, ballot secrecy (often referred to as \term{receipt freeness}) is the most complicated security goal addressed by these systems.

Note that ballot secrecy is of vital importance for several reasons. In countries such as the United
States, it is a fundamental ``right'' that a voter is never required to reveal the candidate for
whom he/she voted. But in some third-world countries, the ability to determine one's chosen
candidate could determine that individual's life or death (e.g., a location in which a malevolent
dictator holds elections as a fa\c{c}ade). Therefore, it is crucial that one not be able to
determine how another voted.

This is also the most interesting goal, as secrecy complicates verifiability. It is only through use
of cryptography that systems such as those we study can provide verifiability without revealing how
individuals' votes were cast.

\subsection{Verifiable recording}

When a voter casts a ballot, he/she knows which candidate(s) he/she \emph{intended} to vote for --
but once the ballot is cast, a system that provides \term{collected-cast-cast verifiability} allows
the voter to compare the recorded vote to what he/she intended to indicate on the ballot.

For example, at an in-person polling location -- ignoring ballot secrecy (see below) -- a voter
could be shown a screen giving the name of the candidate(s) he/she just voted for. If the display
does not match the voter's intention, then the voter can ``try again'' -- or call into question the
entire vote collection process.

\subsection{Verifiable counting}

Once votes have been recorded, it is the responsibility of the state to tally votes for the various
candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
\emph{someone} (e.g., the government at some level) to provide these tallies. But it is much less
common for voters themselves to have the opportunity to verify that the votes were tallied
\emph{exactly} as they were cast.

These systems, however, allow publication of data sufficient to verify tallies. Relying on
cryptography to ensure secrecy, each system involves exposure of cryptographically-hidden vote
counts that can be used to ensure that -- given all votes cast -- the final tallies are correct.

\subsection{Coercion prevention}

Amidst these other goals, it becomes difficult to prevent \term{coercion}: the ability of some party
to coerce (through force, payment, or otherwise) a voter to vote for a particular candidate.

With conventional in-person voting, coercion is thwarted to some extent by the physical security
imposed at polling locations: a party cannot \emph{watch} a voter cast a ballot and so cannot rest
assured that the voter did as told.

Though ballot secrecy prevents such a party from determining that a voter has done as asked, it is a
different problem to ensure that even the voter him/herself cannot prove that his/her ballot was
cast a certain way. We will show, in describing these systems, that the cryptographic techniques
used to provide ballot secrecy also ensure -- in the case of in-person elections -- that a voter
cannot prove his/her ballot was cast a certain way even with the data necessarily exposed to provide
verifiability.

\subsection{True cast ballots only}

While the notions of verifiability presented above allow one to ensure that votes were counted as
they were cast, another problem is to ensure that the body holding the election cannot fabricate
\emph{additional} votes (not actually cast) to raise the tallies as it sees fit.

\section{Scantegrity \cite{scantegrity_ii}}

With Scantegrity (actually Scantegrity II, successor to the original Scantegrity system), each
ballot created is assigned a unique number. While this number can be printed in plain sight, it can
be encrypted such that someone with physical access to a ballot box cannot link a ballot to someone
with a receipt.

Furthermore, each candidate on the ticket -- presented in a consistent manner across tickets (i.e.
no randomization, though some can be used) -- is selected by filling in a ``bubble'' that reveals an
alphanumeric confirmation code: these codes are selected such that they are independent and
uniformly random. On a standard voter ballot, only the codes for candidates selected by the voter
are revealed. The body holding the election -- e.g., the government -- keeps a secret \term{Table P}
that contains all confirmation codes generated for all tickets.

An important point regarding Scantegrity is that it relies on a \emph{physical property} -- the
invisible ink used when printing confirmation code ``bubbles'' -- to combat vote coercion (i.e., no
one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
the person for having voted a certain way).

Scantegrity II does provide -- in their terms:
\begin{enumerate}
	\item
		\term{Voter verifiability} - the ability of a voter to ensure that his/her vote was included in
		the tally; and
	\item
		\term{Universal verifiability} - the ability of \emph{anyone} to verify that, given that some
		set of votes were cast, the candidate counts are correct.
\end{enumerate}

Scantegrity \emph{II} claims to solve some issues with other/previous systems:
\begin{itemize}
	\item
		\term{Pattern voting} and
	\item
		\term{Randomization attacks}, whereby it's possible to tell whether a ballot is actually random
		or is ``biased.''
\end{itemize}

Unfortunately, in order to provide some of its guarantees, Scantegrity II does require a published
list of \emph{who} voted. Such a list could aid groups from penalizing those who do not -- or do --
vote.

At the polling place, a voter may choose to receive a second \term{audit ballot}. This ballot is
marked as such, and all confirmation codes are revealed. The importance of this second ballot will
be revealed below.

The group holding the election generates four tables:
\begin{enumerate}
	\item
		\term{Table P}, which is kept secret and which contains all confirmation codes printed on all
		ballots (along with the corresponding candidate);
	\item
		\term{Table Q}, which is published and which uses scanned information along with Table P to
		reveal -- on a per-ballot basis -- only those confirmation codes which the voter actually
		revealed (including \emph{all} codes for audit ballots).
	\item
		\term{Table R}, which provides a randomly-order but correct bijection from cells in Table Q to
		cells in Table S. After the election has concluded, rows in this table are flagged with a
		boolean ``true'' value if they correspond to codes (Table Q) revealed by the voter on
		\emph{non-audit} ballots. At that time, only one side of the mapping -- to Q or to S -- is
		revealed for non-audit ballots, and which side is revealed is select by a ``true random,
		publicly verifiable coin flip.''
	\item
		\term{Table S}, which provides per-candidate counts by recording in cells, via Table R mappings,
		those codes that were actually revealed on legitimate non-audit ballots.
\end{enumerate}

\todo{Include own image of the tables.}

\todo{Need a much more in-depth discussion of how Scantegrity works. Right now it's a play-by-play
from the source.}

\section{Pr\^{e}t \`{a} Voter}

\section{Helios \cite{helios}}

Overall, Helios performs the following steps in an election:
\begin{enumerate}
	\item
		Encrypt individual votes as they're cast.
	\item
		Mix the votes for privacy.
		\begin{enumerate}
    	\item
				Re-encrypt the ballots (ElGamal).
    	\item
				Shuffle using a \term{mixnet}.
			\item
				Give cryptographic proof of a legitimate shuffle.
			\item
				Decrypt the votes.
			\item
				Give cryptographic proof of the decryptions.
		\end{enumerate}
	\item
		Tally the votes.
\end{enumerate}

Helios relies on auditing at two stages: (a) by voters when casting ballots and (b) by independent
auditors after votes have been tallied.

After entering one's candidate choices, but before a vote is actually cast, a voter is presented
with a (SHA-1) hash of his/her encrypted vote and can choose to ``audit'' the ballot, in which case
Helios will reveal all the information necessary (including ``randomness'') for the voter to verify
that the hash correctly represents the vote he/she indended to cast. A voter can continue to audit
ballots (due to randomness, different each time) before casting one. He/she is \emph{not} given the
information necessary to audit the ballot that is ultimately cast.

Once votes have been tallied at the end of the election, auditors can obtain all data from the
election -- except for the secret keys necessary for shuffling and encryption but (notably)
including the generated proofs -- to verify that the votes were counted correctly. These auditors
can post their verifications publicly and compare results with other auditors.

It is important to note -- and the Helios researchers note this -- that this hinges on active
involvement from the community.

The ballot shuffle and decryption are proved using a technique called an \term{Honest-Verifier
Zero-Knowledge} proof. However, because the challenges in Helios are generated without human
involvement, a technique called Fiat-Shamir is used to obtain a hash (so $\code{0}$s and
$\code{1}$s) that are treated as the challenges.

\todo{Need a much more in-depth discussion of how Helios works. Right now it's a play-by-play from
the source.}

\section{Analysis}

\subsection{Ballot secrecy}

Each of these systems provides ballot secrecy by performing a three-step process:
\begin{enumerate}
	\item
		Encrypt ballot prior to its being cast.
	\item
		``Mix'' the ballots in some way.
	\item
		Reveal decrypted ballots for tallying.
\end{enumerate}

\subsubsection{Encryption}

In both Scantegrity and Helios, the following information is revealed after the election:
\begin{itemize}
	\item
		\emph{Some} information about \emph{all} encrypted ballots, linked to voters.
	\item
		\emph{All} decrypted ballots, emph{not} linked to voters.
\end{itemize}

In Scantegrity, ``public'' version of a ballot is really just an encryption of the voter's
selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
particular candidate for that ballot. Table P defines an explicit, ``keyless'' encryption
function -- and each ballot holds just enough information from Table P to encrypt a single voter's
responses.

In Helios, the ``public'' ballot is a hash of an encryption. Helios uses ElGamal to encrypt ballots,
which -- unlike Scantegrity's core \emph{random} Table P -- could be subject to attack, given that
ElGamal is a published encryption function. Similarly, Helios uses the standard SHA-1 hash algorithm
to hash encrypted ballots. Note that we are not making a precise quantification about Helios's
security: rather, we simply note that the difference between these two systems can be thought of as
a tradeoff between key size and privacy guarantees. Scantegrity essentially has an immensely large
key that -- because it is theoretically completely random -- ensures that ciphertext cannot be
decrypted. Helios, however, uses known algorithms with shorter keys that could potentially be
attacked. Compromise of keys in either system would destroy their privacy guarantees.

\todo{We can also talk about Scantegrity's Table P as a definition wherein the ballot number is the
key.}

\subsubsection{Mixing}

Essentially, both Scantegrity and Helios use some mechanism to ``shuffle'' votes so that -- even
with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
counterparts.

In Scantegrity, the ballot ``mix'' is predetermined, as it is defined by the generation of Table R.
When that table is constructed, ballots are randomly \todo{Really?} ordered. With the exception of
audit ballots, the information revealed that is ultimately revealed allows half of the ballots to be
traced only from Table Q to Table R; and the other half can only be traced from Table R to Table S.
Should Table P be compromised, one could complete all mappings and violate secrecy entirely -- or
simply decrypt encrypted votes with no attention giving to Table R. Should the mapping on
\emph{either} size of Table R (to votes in Table Q or tallies in Table S) be deterministic, privacy
would be compromised for half of all voters.

Where Table R lies between encryptions and decryptions in Scantegrity, Helios makes use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in Scantegrity, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally.

At a high level, the difference between these two schemes is in the number of mappings that must be
kept secret in order to ensure ballot secrecy. In Scantegrity, Table R has one mapping to Table Q
and a second to Table S, and neither of these can be compromised to ensure secrecy for all ballots.
But in Helios, use of a cryptographic mixnet means that both inputs and outputs can be mapped to
voters and tallies, respectively, without revealing the inner mapping. In some ways, Helios's
approach accomplishes the same goals as \emph{but} is implemented as an anthesis of Scantegrity's
Table system.

\todo{Include image showing difference between Scantegrity and Helios voting mappings.}

It is important that we have considered secrecy mechanisms first, as these strategies enable
fulfillment of other goals, such as \emph{verifiability}.

\subsection{Verifiable recording}

\subsection{Verifiable counting}

\subsection{Coercion prevention}

Scantegrity prevents coercion via the manner it uses to ``encrypt'' ballots. Once cast, a ballot's
ciphertext is \emph{always public}. A voter can claim that he/she voted in a particular manner, but
without exposure of the data maintained in Table P -- Scantegrity's ``secret'' -- the voter has no
way to prove to a third party that the claim is true. This is

Helios, which is designed for use in an online setting, has no illusions about coercion: in fact,
the public implementation makes it clear to voters that they would be easy to coerce. Setting
(physical security) aside: as with Scantegrity, Helios does not reveal to a voter all the
information necessary to \emph{prove} a decryption of his/her ballot. Though a voter is able to see
encryption details for ballots chosen for audit, that information is never displayed to the user
when finally casting a ballot. Furthermore, even if it were, it is possible (though perhaps
unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
data) that would produce the same hash but for a different candidate, thus ``proving'' something
untrue to the coercing party. (This is one reason that it is important for the system to use a
collision-resistant hash function.)

\subsection{True cast ballots only}

Note that each of these systems rely on publication of some information for every ballot that was
cast (whether it be the entire encrypted ballot or a hash of the ballot).

The public nature of htis information can combat ``ballot stuffing.'' If names are associatd with
the posted ballots, then it should be obvious to one or more careful observers (given sufficient
resources) that nonexistent persons are being posted. Furthermore, publiction of ballots
per-precinct can reveal ``stuffing'' should the number of ballots being reported by a particular
precinct/polling location be significantly higher than expected \cite{helios}.

\section{Other considerations}

\subsection{Identity of (non-)voters}

One might wish to prevent a party from determining who did or did not cast \emph{any} ballot.
As we've seen, \term{verifiable counting} typically relies on the ``public'' nature of this data.
Additionally, should this data be hidden, it could potentially be more difficult to notice ``ballot
stuffing'' (discussed above above).

One potential solution to this, taken by some systems \cite{preta}, is to reveal ballot identifiers
rather than voter names. This does make detection of ballot stuffing more difficult and does not get
around the fact that at some level, \emph{someone} must possess a list of voters to prevent double
voting.

\subsection{Keeping secrets}

In each of these key systems, there exists some way to tie a vote back to a voter: there is always
some secret. Ideally, there would be a system wherein a vote could be tallied properly (somehow)
without being able to reveal who the vote was for. (Admittedly, that would be difficult: if that is
the only vote, then ``tallying'' just it would reveal the candidate for which it was cast.)

But it would be a worthy goal at least to minimize (if not eliminate) the amount of data that must
be kept secret. Usually it is one or two pieces of data -- and these systems attempt to mitigate
risk by requiring that multiple entities (persons) be present in order to access that secret data.

With each of these systems, there is \emph{still} a significant level of trust placed in the body
holding the election. This is the issue with secrets: \emph{someone} must keep them.

In order for a voting system to be \emph{useful}, it must be feasible given the nature of society
today, and so solutions that rely on, say, personally-maintained keypairs are outside the scope of
a practical system.

In the end, there are as yet no \emph{perfect} verifiable voting systems that achieve both complete
privacy and completely verifiable integrity, as there are always attack vectors (often physical
ones). This has not been seen as a problem by researchers in the past, as physical security is
indeed outside the scope of these systems as they have been developed; but perhaps with further
research into advanced cryptographic schemes we can someday eliminate any state-held secret data and
yet hold a completely verifiable election.

\subsection{Randomness}

It is clear that Scantegrity's secrets -- Tables P and R -- are generated using a source of true
randomness. If there is any detrminism in generating those tables, an attacker could exploit the
generation method to violate privacy. Helios, on the other hand, was designed with application in
mind and therefore uses standard crytographic techniques (e.g., ElGamal and SHA-1).

Given a flawless implementation of Scantegrity as specified in research, it can certaily provide the
security it claims. However, we note that an amateur implementation of the protocol laid out by
Scantegrity's creators -- e.g., one that uses a nonperfect source of randomization -- could lead to
a very insecure system.

The same can be said for Helios, should it be implemented with inappropriate primitives (not ElGamal
and SHA-1); however, as the authors have designed the scheme with particular primitives in mind, its
specification is less open to interpretation (and thus potentially harmful choices).

\section{Conclusion}

\bibliography{sources}{}
\bibliographystyle{plain}

\end{multicols}

\end{document}

% vim: set inde= colorcolumn=101 textwidth=100:

### 2012-12-05 paper/paper.tex
Rework descriptions, some analysis, and add topics
Reworked (largely rewrote) system descriptions for Scantegrity and
Helios.

Did some work (though not much) on the analysis -- in part, moving text
that I had elsewhere in the paper.

Added some new topics for discussion.

Also introduced distinction between verifiable recording and verifiable
collection (as discussed face-to-face and as pointed out in the Prêt à
Voter paper).

@@
 % title
-\title{Cryptographic assurance of fairness in voting}
+\title{Cryptographic assurance of secrecy and fairness in voting}
 \date{}
@@
 
-When a voter casts a ballot, he/she knows which candidate(s) he/she \emph{intended} to vote for --
-but once the ballot is cast, a system that provides \term{collected-cast-cast verifiability} allows
-the voter to compare the recorded vote to what he/she intended to indicate on the ballot.
+When casting a ballot, a voter knows which candidate(s) he/she \emph{intended} to vote for -- but
+once the ballot is cast, a system that supports verification of vote reporting allows the voter to
+compare the recorded vote to what he/she intended to indicate on the ballot.
 
@@
 
+\subsection{Verifiable collection}
+
+After a ballot has been cast, and the voter has left the polling place, how can he/she be certain
+that the ballot used in the final count is what he/she actually cast? (This could be a problem even
+if the user has verified the \emph{recording} of the vote.)
+
+It is possible -- as we shall see -- for a voting system to allow a voter to check that the ballot
+he/she cast is exactly what was considered during vote counting.
+
 \subsection{Verifiable counting}
 
-Once votes have been recorded, it is the responsibility of the state to tally votes for the various
+Once votes have been collected, it is the responsibility of the state to tally votes for the various
 candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
@@
 
-\section{Scantegrity \cite{scantegrity_ii}}
+\section{Scantegrity}
 
-With Scantegrity (actually Scantegrity II, successor to the original Scantegrity system), each
-ballot created is assigned a unique number. While this number can be printed in plain sight, it can
-be encrypted such that someone with physical access to a ballot box cannot link a ballot to someone
-with a receipt.
+The Scantegrity system \cite{scantegrity_ii} (technically, we consider an updated version known as
+Scantegrity II) is designed to provide verifiability atop existing in-person voting systems that
+rely on fill-in ballots that are processed via optical scan.
 
-Furthermore, each candidate on the ticket -- presented in a consistent manner across tickets (i.e.
-no randomization, though some can be used) -- is selected by filling in a ``bubble'' that reveals an
-alphanumeric confirmation code: these codes are selected such that they are independent and
-uniformly random. On a standard voter ballot, only the codes for candidates selected by the voter
-are revealed. The body holding the election -- e.g., the government -- keeps a secret \term{Table P}
-that contains all confirmation codes generated for all tickets.
+\subsection{Before voting}
 
-An important point regarding Scantegrity is that it relies on a \emph{physical property} -- the
-invisible ink used when printing confirmation code ``bubbles'' -- to combat vote coercion (i.e., no
-one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
-the person for having voted a certain way).
+Before an election is held, the body holding the election (e.g., the government) must construct four
+Tables that lie at the core of the Scantegrity system: Tables P, Q, R, and S.
 
-Scantegrity II does provide -- in their terms:
+Some selection of persons associated with the electing body use a secret-sharing scheme to protect a
+secret pseudorandom number generator key. Table P lists every ballot that will be produced for the
+election and specifies exactly what code (which we'll see later) is used for each candidate per
+ballot. These codes are generated using the pseudorandom generator and \emph{must} be kept secret.
+
+Table Q has one row per ballot, as in Table P, but the codes presented on that ballot are included
+in randomly-ordered cells so that a particular code cannot be mapped to a particular candidate.
+Once ballots have been collected, only the cell actually marked on each ballot is revealed. (Note
+that the column shuffle must be per-row, as otherwise one could determine whether two voters
+cast a vote for the same candidate.)
+
+Table S contains final vote tallies. Each column represents a particular candidate, and there will
+be one ``checked'' cell in each column for each ballot cast for that candidate.
+
+Table R is the ``heart'' of the Scantegrity Tables: it maps cast ballots in Table Q to tally marks
+in Table S. Each row in Table R maps a single cell in Q to a single cell in S, and the order of
+these mappings is pseudorandom (though the mappings must obey the data specified in Table P for vote
+correctness).
+
+\todo{Include our own depiction of the tables in an image.}
+
+\subsection{Voting}
+
+A Scantegrity ballot consists of two portions: a special optical-scan ballot strip and a second
+piece of paper that the voter will keep as a receipt. Each ballot is identified by a unique number,
+which is printed on both portions. (While this nuber can be printed in plain sight, it can also be
+encrypted on the optical-scan portion such that someone with physical access to a ballot box cannot
+link a particular ballot to a voter with receipt in-hand.)
+
+All candidates are listed on the optical-scan ballot, and the voter makes his/her choice by filling
+in a ``bubble'' that reveals an alphanumeric confirmation code (as specified in the private Table
+P), which the voter then records on the receipt portion. The ballot is sent through an optical
+scanner, and the voter takes his/her receipt when leaving the polling location. It can later be
+compared against published Table Q to ensure that the vote was recorded properly.
+
+Additionally, during the voting process, a voter can ask a poll worker for an second ``audit''
+ballot. This ballot is initially just like any other ballot: however, \emph{all} candidate codes are
+revealed, and the ballot is marked as an audit ballot. An audit ballot is scanned, but the voter is
+allowed to keep the ballot for later verification.
+
+\subsection{After voting}
+
+When a ballot has been received, the following takes place:
 \begin{enumerate}
 	\item
-		\term{Voter verifiability} - the ability of a voter to ensure that his/her vote was included in
-		the tally; and
+		The candidate code is revealed in Table Q. (If this is an audit ballot -- see below -- then all
+		are revealed, and we'll perform the following steps for each code.)
 	\item
-		\term{Universal verifiability} - the ability of \emph{anyone} to verify that, given that some
-		set of votes were cast, the candidate counts are correct.
+		A ``check'' is placed on the row in Table R that maps the revealed Q value to some value in S.
+	\item
+		The Table R mapping is followed into Table S, and a ``check'' is added to a cell in Table R
+		(to be counted as a vote for that row's candidate).
 \end{enumerate}
 
-Scantegrity \emph{II} claims to solve some issues with other/previous systems:
-\begin{itemize}
-	\item
-		\term{Pattern voting} and
-	\item
-		\term{Randomization attacks}, whereby it's possible to tell whether a ballot is actually random
-		or is ``biased.''
-\end{itemize}
+Tables Q and S and published in their entirety. However, one member of each Q-to-S cell mapping pair
+is hidden prior to its publication (except for audit ballots, for which both sides of the mapping
+are revealed). This data is required for third-party verification.
 
-Unfortunately, in order to provide some of its guarantees, Scantegrity II does require a published
-list of \emph{who} voted. Such a list could aid groups from penalizing those who do not -- or do --
-vote.
-
-At the polling place, a voter may choose to receive a second \term{audit ballot}. This ballot is
-marked as such, and all confirmation codes are revealed. The importance of this second ballot will
-be revealed below.
-
-The group holding the election generates four tables:
-\begin{enumerate}
-	\item
-		\term{Table P}, which is kept secret and which contains all confirmation codes printed on all
-		ballots (along with the corresponding candidate);
-	\item
-		\term{Table Q}, which is published and which uses scanned information along with Table P to
-		reveal -- on a per-ballot basis -- only those confirmation codes which the voter actually
-		revealed (including \emph{all} codes for audit ballots).
-	\item
-		\term{Table R}, which provides a randomly-order but correct bijection from cells in Table Q to
-		cells in Table S. After the election has concluded, rows in this table are flagged with a
-		boolean ``true'' value if they correspond to codes (Table Q) revealed by the voter on
-		\emph{non-audit} ballots. At that time, only one side of the mapping -- to Q or to S -- is
-		revealed for non-audit ballots, and which side is revealed is select by a ``true random,
-		publicly verifiable coin flip.''
-	\item
-		\term{Table S}, which provides per-candidate counts by recording in cells, via Table R mappings,
-		those codes that were actually revealed on legitimate non-audit ballots.
-\end{enumerate}
-
-\todo{Include own image of the tables.}
-
-\todo{Need a much more in-depth discussion of how Scantegrity works. Right now it's a play-by-play
-from the source.}
+This process will be discussed further in the analysis.
 
@@
 
-\section{Helios \cite{helios}}
+\todo{Fill in.}
 
-Overall, Helios performs the following steps in an election:
-\begin{enumerate}
-	\item
-		Encrypt individual votes as they're cast.
-	\item
-		Mix the votes for privacy.
-		\begin{enumerate}
-    	\item
-				Re-encrypt the ballots (ElGamal).
-    	\item
-				Shuffle using a \term{mixnet}.
-			\item
-				Give cryptographic proof of a legitimate shuffle.
-			\item
-				Decrypt the votes.
-			\item
-				Give cryptographic proof of the decryptions.
-		\end{enumerate}
-	\item
-		Tally the votes.
-\end{enumerate}
+\section{Helios}
 
-Helios relies on auditing at two stages: (a) by voters when casting ballots and (b) by independent
-auditors after votes have been tallied.
+Helios \cite{helios} -- unlike Scantegrity and Pr\^{e}t \`{a} Voter -- is an \emph{online} voting
+system that attempts to meet many of the same goals (namely, verifiability).
 
-After entering one's candidate choices, but before a vote is actually cast, a voter is presented
-with a (SHA-1) hash of his/her encrypted vote and can choose to ``audit'' the ballot, in which case
-Helios will reveal all the information necessary (including ``randomness'') for the voter to verify
-that the hash correctly represents the vote he/she indended to cast. A voter can continue to audit
-ballots (due to randomness, different each time) before casting one. He/she is \emph{not} given the
-information necessary to audit the ballot that is ultimately cast.
+\subsection{Before voting}
 
-Once votes have been tallied at the end of the election, auditors can obtain all data from the
-election -- except for the secret keys necessary for shuffling and encryption but (notably)
-including the generated proofs -- to verify that the votes were counted correctly. These auditors
-can post their verifications publicly and compare results with other auditors.
+At the heart of Helios is a single ElGamal keypair. The secret key is known only to the Helios
+server, but the public key can (by its nature) be accessed in some way by all participants.
 
-It is important to note -- and the Helios researchers note this -- that this hinges on active
-involvement from the community.
+\subsection{Voting}
 
-The ballot shuffle and decryption are proved using a technique called an \term{Honest-Verifier
-Zero-Knowledge} proof. However, because the challenges in Helios are generated without human
-involvement, a technique called Fiat-Shamir is used to obtain a hash (so $\code{0}$s and
-$\code{1}$s) that are treated as the challenges.
+When a voter goes to cast a vote, his/her candidate selection is encrypted locally (i.e., on his/her
+computer terminal, in the browser) using ElGamal. Prior to casting the ballot, the voter is
+presented with a SHA-1 hash of his/her encrypted ballot. At this point, the voter may choose either
+to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
+complete. But when a voter chooses to ``audit,'' he/she is presented with \emph{all} of the data
+used to encrypt the vote. Namely, this includes the public key and the ``randomness'' that were used
+by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
+(one which allows randomness to be specified) -- perform the encryption and SHA-1 hash him/herself
+to verify that the hash that \emph{would} have been cast actually does represent the ballot he/she
+intended to cast.
 
-\todo{Need a much more in-depth discussion of how Helios works. Right now it's a play-by-play from
-the source.}
+\subsection{After voting}
+
+Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
+``mixnet.'' \todo{We should discuss re-encryption details, which are covered in the Helios paper.
+Maybe we cover the details in the Pr\^{e}t \`{a} Voter discussion?}
+
+The ``mixnet'' accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
+same key, but with different random inputs). A random permutation -- referred to as $\pi_{N}$ (where
+$N$ is the total number of votes) -- is first used to perform the shuffle. Each ciphertext 
+$c_{i}$ is then ``re-encrypted'' to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
+the random input at encrypt time been different} by a particular amount $s_{i}$.
+
+The ``shuffling'' is important because it prevents an attacker (or simple onlooker) from linking
+a decrypted ballot with a particular encrypted ballot -- and thus a voter. Re-encryption means that
+an auditor examining a proof of proper decryption (see below) cannot determine how a particular
+voter cast his/her ballot by hashing all ciphertexts in the proof and matching those hashes to the
+publicly-posted encrypted vote hashes.
+
+Finally, votes are decrypted and tallied. At this time, Helios also publishes the information
+necessary for anyone who wishes to audit the election to verify that the mixnet's shuffling and
+decryption were performed properly.
+
+In order to provide a guarantee of proper shuffling, Helios actually shuffles the votes multiple
+times, actually using only the final shuffle in tallying the results. The other shuffles are
+referred to as ``shadow mixes'' and are made public. Those mixes are hashed to obtain a bit string
+that is used, bit-for-bit, as a set of challenges, with one bit value indicating that Helios must
+provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the 
+other bit value indiciating that it must provide a mapping from one shadow mix to another. This is
+known as an ``Honest-Verifier Zero-Knowlege'' proof, for which the probability that the final
+product is correct is equal to $1 - 2^{t}$, where $t$ is the number of shadow mixes produced.
+
+Similarly, the Chaum-Peterson zero-knowledge proof technique is used to prove that decryption is
+correct. \todo{How much detail should we provide?}
 
 \section{Analysis}
+
+We will analyze these voting systems by considering each security goal in turn.
 
@@
 	\item
-		\emph{All} decrypted ballots, emph{not} linked to voters.
+		\emph{All} decrypted ballots, \emph{not} linked to voters.
 \end{itemize}
@@
 function -- and each ballot holds just enough information from Table P to encrypt a single voter's
-responses.
+responses. (Alternatively, one can think of Table P as an encryption scheme definition wherein the
+ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
+compromise would eliminate ballot secrecy for all ballots.)
 
@@
 
-\todo{We can also talk about Scantegrity's Table P as a definition wherein the ballot number is the
-key.}
-
 \subsubsection{Mixing}
@@
 In Scantegrity, the ballot ``mix'' is predetermined, as it is defined by the generation of Table R.
-When that table is constructed, ballots are randomly \todo{Really?} ordered. With the exception of
-audit ballots, the information revealed that is ultimately revealed allows half of the ballots to be
+When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
+ballots, the information revealed that is ultimately revealed allows half of the ballots to be
 traced only from Table Q to Table R; and the other half can only be traced from Table R to Table S.
@@
 
+At the time a ballot is cast, both Scantegrity and Helios attempt to ensure a voter that his/her
+vote is recorded exactly as intended.
+
+In Scantegrity, this verification is rolled into the ballot casting process. After recording the
+receipt him/herself, a voter can visually check that the code on the receipt matches the candidates
+selected on the ballot.
+
+Helios does not actually permit a voter to verify the ballot that he/she actually casts. Rather, it
+allows users to verify a ballot without casting it (after which point it cannot be cast without
+a new encryption). The assumption here is that \emph{some} voter will choose to audit a ballot, and
+so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
+one -- otherwise the deception would be revealed should the voter choose to exercise his/her right
+to audit.
+
+While both systems provide the voter some assurance that the proper vote was recorded, Scantegrity's
+verification process is more direct and provides a stronger guarantee that the ballot \emph{actually
+cast} was recorded properly.
+
+\subsection{Verifiable collection}
+
+A common theme in verifiable voting systems seems to be the presence of a published ``bulletin
+board'' of votes. (Note that because these boards contain only encrypted information, they do not
+violate ballot secrecy.)
+
+In the case on Scantegrity, this information is primarily embodied in the published version of Table
+Q. After the election, a voter can compare his/her receipt code with that revealed for his ballot in
+Table Q. If the code does not match, then something is amiss.
+
+Helios, similarly, exposes a complete list of ballot hashes. A voter can examine this data set to
+ensure that it accurately reflects the hash that was reported on screen when the ballot was cast.
+
 \subsection{Verifiable counting}
+
+\todo{Fill in.}
 
@@
 without exposure of the data maintained in Table P -- Scantegrity's ``secret'' -- the voter has no
-way to prove to a third party that the claim is true. This is
+way to prove to a third party that the claim is true.
+
+An important point regarding Scantegrity is that it also relies on a \emph{physical property} -- the
+invisible ink used when printing confirmation code ``bubbles'' -- to combat vote coercion (i.e., no
+one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
+the person for having voted a certain way). This is akin to keeping Table P a secret: the ballots
+together \emph{are} Table P, and using special ink allows the codes to be printed without making it
+easy for a ballot handler to simple read Table P from the ballots prior to the election.
 
@@
 \section{Other considerations}
+
+\subsection{Clever attacks on verifiable voting systems}
+
+Scantegrity \emph{II} claims to solve some issues with other/previous systems:
+\begin{itemize}
+	\item
+		\term{Pattern voting} and
+	\item
+		\term{Randomization attacks}, whereby it's possible to tell whether a ballot is actually random
+		or is ``biased.''
+\end{itemize}
+
+\subsection{Voter involvement}
+
+It is important to note -- and the Helios researchers note this -- that this hinges on active
+involvement from the community.
 
@@
 
+\todo{Remark on the fact that the election itself has a single primary ElGamal keypair.}
+
 \subsection{Randomness}
@@
 
+\todo{Fill in.}
+
 \bibliography{sources}{}

### 2012-12-05 paper/paper.tex
Add \pv{} command as a shortcut for Pret a Voter.

@@
 \newcommand{\sub}[1]{\textsubscript{#1}}
+\newcommand{\preta}{Pr\^{e}t \`{a}}
+\newcommand{\pv}{\preta{} Voter}
 
@@
 	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
-	how three popular verifable voting systems -- Scantegrity, Pr\^{e}t \`{a} Voter, and Helios --
+	how three popular verifable voting systems -- Scantegrity, \pv{}, and Helios --
 	use cryptographic techniques to meet those goals.
@@
 In this survey, we will study three of the most well-known solutions: the in-person voting systems
-Scantegrity and Pr\^{e}t \`{a} Voter and the online voting system Helios.
+Scantegrity and \pv{} and the online voting system Helios.
 
@@
 
-\section{Pr\^{e}t \`{a} Voter}
+\section{\pv{}}
 
@@
 
-Helios \cite{helios} -- unlike Scantegrity and Pr\^{e}t \`{a} Voter -- is an \emph{online} voting
+Helios \cite{helios} -- unlike Scantegrity and \pv{} -- is an \emph{online} voting
 system that attempts to meet many of the same goals (namely, verifiability).
@@
 ``mixnet.'' \todo{We should discuss re-encryption details, which are covered in the Helios paper.
-Maybe we cover the details in the Pr\^{e}t \`{a} Voter discussion?}
+Maybe we cover the details in the \pv{} Voter discussion?}
 

### 2012-12-05 paper/paper.tex
Add \nonstopmode.
Rename sources.bib to paper.bib. Add real citation for Pret a Voter. Change bibtex style to IEEETran.
whitespace
Fix spelling errors.

@@
 	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
-	how three popular verifable voting systems -- Scantegrity, \pv{}, and Helios --
+	how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
 	use cryptographic techniques to meet those goals.
@@
 piece of paper that the voter will keep as a receipt. Each ballot is identified by a unique number,
-which is printed on both portions. (While this nuber can be printed in plain sight, it can also be
+which is printed on both portions. (While this number can be printed in plain sight, it can also be
 encrypted on the optical-scan portion such that someone with physical access to a ballot box cannot
@@
 provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
-other bit value indiciating that it must provide a mapping from one shadow mix to another. This is
-known as an ``Honest-Verifier Zero-Knowlege'' proof, for which the probability that the final
+other bit value indicating that it must provide a mapping from one shadow mix to another. This is
+known as an ``Honest-Verifier Zero-Knowledge'' proof, for which the probability that the final
 product is correct is equal to $1 - 2^{t}$, where $t$ is the number of shadow mixes produced.
@@
 voters and tallies, respectively, without revealing the inner mapping. In some ways, Helios's
-approach accomplishes the same goals as \emph{but} is implemented as an anthesis of Scantegrity's
+approach accomplishes the same goals as \emph{but} is implemented as an antithesis of Scantegrity's
 Table system.
@@
 
-The public nature of htis information can combat ``ballot stuffing.'' If names are associatd with
+The public nature of this information can combat ``ballot stuffing.'' If names are associated with
 the posted ballots, then it should be obvious to one or more careful observers (given sufficient
-resources) that nonexistent persons are being posted. Furthermore, publiction of ballots
+resources) that nonexistent persons are being posted. Furthermore, publication of ballots
 per-precinct can reveal ``stuffing'' should the number of ballots being reported by a particular
@@
 It is clear that Scantegrity's secrets -- Tables P and R -- are generated using a source of true
-randomness. If there is any detrminism in generating those tables, an attacker could exploit the
+randomness. If there is any determinism in generating those tables, an attacker could exploit the
 generation method to violate privacy. Helios, on the other hand, was designed with application in
-mind and therefore uses standard crytographic techniques (e.g., ElGamal and SHA-1).
+mind and therefore uses standard cryptographic techniques (e.g., ElGamal and SHA-1).
 
-Given a flawless implementation of Scantegrity as specified in research, it can certaily provide the
+Given a flawless implementation of Scantegrity as specified in research, it can certainly provide the
 security it claims. However, we note that an amateur implementation of the protocol laid out by
-Scantegrity's creators -- e.g., one that uses a nonperfect source of randomization -- could lead to
+Scantegrity's creators -- e.g., one that uses a non-perfect source of randomization -- could lead to
 a very insecure system.
@@
 
-\bibliography{sources}{}
-\bibliographystyle{plain}
+\bibliographystyle{IEEEtran}
+\bibliography{paper}
 

### 2012-12-05 paper/paper.tex
Enable spell checking in Vim (modeline)
Describe "roles" from Preta, rewrite secrecy intro

@@
 
-A ``verifiable'' election is one in which the voters may rest assured that the body holding the
-election (e.g., a government) reports final vote tallies that exactly reflect votes as they were
-cast by the electorate.
+An election involves an information exchange between many independent \term{voters} and a single
+\term{election authority} organization.
+In a verifiable election, each voter may verify that her own vote was counted correctly
+by the election authority.
+A voter, or any other third party \term{auditor}, may also verify the accuracy of the final tallies
+reported by the election authority. \cite{preta}
 
@@
 
-In many ways, ballot secrecy (often referred to as \term{receipt freeness}) is the most complicated security goal addressed by these systems.
+Countries such as the United States hold as a fundamental right that voting can be performed
+in secret to reduce the possibility of voter coercion from any private entities.
+In some developing states where corruption is prevalent, it may be desirable keep an
+individual's vote hidden even from the election authority, again for the reason of
+limiting coercibility. The latter goal is significantly more restrictive.
 
-Note that ballot secrecy is of vital importance for several reasons. In countries such as the United
-States, it is a fundamental ``right'' that a voter is never required to reveal the candidate for
-whom he/she voted. But in some third-world countries, the ability to determine one's chosen
-candidate could determine that individual's life or death (e.g., a location in which a malevolent
-dictator holds elections as a fa\c{c}ade). Therefore, it is crucial that one not be able to
-determine how another voted.
-
-This is also the most interesting goal, as secrecy complicates verifiability. It is only through use
-of cryptography that systems such as those we study can provide verifiability without revealing how
-individuals' votes were cast.
+Ballot secrecy, often referred to as \term{receipt-freeness}, is perhaps the most complicated
+security goal to address in a verifiable voting system.
+Secrecy and verifiability are naturally at odds, and only through cryptography can we
+reconcile these two requirements.
 
@@
 security it claims. However, we note that an amateur implementation of the protocol laid out by
-Scantegrity's creators -- e.g., one that uses a non-perfect source of randomization -- could lead to
-a very insecure system.
+Scantegrity's creators -- e.g., one that uses a imperfect source of randomization -- could lead to a
+very insecure system.
 
@@
 
-% vim: set inde= colorcolumn=101 textwidth=100:
+% vim: set inde= colorcolumn=101 textwidth=100 spell:

### 2012-12-05 paper/paper.tex
Move coercion section next to secrecy
restructure Background into Verifiability and Secrecy sections

--- 2012-12-05 paper/paper.tex
@@
 % don't number sections
-\setcounter{secnumdepth}{0}
+%\setcounter{secnumdepth}{0}
 
@@
 
-\section{Background}
-
 An election involves an information exchange between many independent \term{voters} and a single
 \term{election authority} organization.
-In a verifiable election, each voter may verify that her own vote was counted correctly
+In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
 by the election authority.
@@
 reported by the election authority. \cite{preta}
+Voting is complicated by the requirement that all votes be secretive to avoid coercion.
 
-\subsection{Ballot secrecy}
-
-Countries such as the United States hold as a fundamental right that voting can be performed
-in secret to reduce the possibility of voter coercion from any private entities.
-In some developing states where corruption is prevalent, it may be desirable keep an
-individual's vote hidden even from the election authority, again for the reason of
-limiting coercibility. The latter goal is significantly more restrictive.
-
-Ballot secrecy, often referred to as \term{receipt-freeness}, is perhaps the most complicated
-security goal to address in a verifiable voting system.
-Secrecy and verifiability are naturally at odds, and only through cryptography can we
-reconcile these two requirements.
+\section{Verifiability}
 
@@
 
-\subsection{Coercion prevention}
+\subsection{True cast ballots only}
+
+While the notions of verifiability presented above allow one to ensure that votes were counted as
+they were cast, another problem is to ensure that the body holding the election cannot fabricate
+\emph{additional} votes (not actually cast) to raise the tallies as it sees fit.
+
+\section{Ballot secrecy}
+
+It is often necessary to maintain secrecy of invididuals' votes, to avoid the possibility
+that a voter may receive either retribution or reward.
+We give two definitions of ballot secrecy: \term{privacy} and \term{receipt-freeness}.
+
+\subsection{Privacy}
+
+\subsection{Receipt-freeness}
+
+\subsection{Stuff that will be moved into one of the previous sections}
+
+Countries such as the United States hold as a fundamental right that voting can be performed
+in secret to reduce the possibility of voter coercion from any private entities.
+In some developing states where corruption is prevalent, it may be desirable keep an
+individual's vote hidden even from the election authority, again for the reason of
+limiting coercibility. The latter goal is significantly more restrictive.
+
+Ballot secrecy, often referred to as \term{receipt-freeness}, is perhaps the most complicated
+security goal to address in a verifiable voting system.
+Secrecy and verifiability are naturally at odds, and only through cryptography can we
+reconcile these two requirements.
 
@@
 verifiability.
-
-\subsection{True cast ballots only}
-
-While the notions of verifiability presented above allow one to ensure that votes were counted as
-they were cast, another problem is to ensure that the body holding the election cannot fabricate
-\emph{additional} votes (not actually cast) to raise the tallies as it sees fit.
 

### 2012-12-05 paper/paper.tex
Add coercion resistance

@@
 
-It is often necessary to maintain secrecy of invididuals' votes, to avoid the possibility
-that a voter may receive either retribution or reward.
-We give two definitions of ballot secrecy: \term{privacy} and \term{receipt-freeness}.
+The intent of an election is to determine the true will of the voters.
+If there is any possibility for a third party to discover the content of
+an individual's ballot, then the voter's own will may be undermined by coercion.
+Therefore a voting system must maintain secrecy of invididuals' votes to avoid
+the possibility that a voter may receive retribution or reward for casting a vote
+in any particular way.
+
+We give multiple definitions of ballot secrecy in order of increasing strength:
+\term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.
 
@@
 \subsection{Receipt-freeness}
+
+\subsection{Coercion resistance}
 

### 2012-12-05 paper/paper.tex
Add Delaune citation for secrecy definitions
Remove empty citation command.
Vaguely start a formal notion of privacy

@@
 
-We give multiple definitions of ballot secrecy in order of increasing strength:
+Delaune \cite{delaune} gives several definitions of ballot secrecy.
+In order of increasing strength, they are
 \term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.
@@
 \subsection{Privacy}
+
+Privacy addresses information that is revealed by the system itself.
+A system is private if a voter who wants to keep her vote secret is able to do so.
+In a verifiable voting system, the system includes the verification process.
+So in addition to casting a vote in private, the voter must also be able to
+audit her vote without revealing its content.
+
+More formally, we can say that an election system has private ballots
+if a reasonably time-bounded attacker, having access to the public information
+published by the polling authority ... \todo{}
 

### 2012-12-06 paper/paper.tex
Adjust whitespace in \author

@@
   \begin{tabular}{c c c}
-Kelsey Francis & Curtis Free & Christopher Martin \\
-\small \tt{francis@gatech.edu} & \small \tt{curtis.free@gatech.edu} & \small \tt{chris.martin@gatech.edu}
+    Kelsey Francis &
+    Curtis Free &
+    Christopher Martin \\
+    \small \tt{francis@gatech.edu} &
+    \small \tt{curtis.free@gatech.edu} &
+    \small \tt{chris.martin@gatech.edu}
   \end{tabular}
@@
 candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
-\emph{someone} (e.g., the government at some level) to provide these tallies. But it is much less
-common for voters themselves to have the opportunity to verify that the votes were tallied
-\emph{exactly} as they were cast.
+\emph{someone} to provide these tallies. But it is much less common for voters themselves to have
+the opportunity to verify that the votes were tallied \emph{exactly} as they were cast.
 
@@
 they were cast, another problem is to ensure that the body holding the election cannot fabricate
-\emph{additional} votes (not actually cast) to raise the tallies as it sees fit.
+\emph{additional} uncast votes to raise the tallies as it sees fit.
 
@@
 Amidst these other goals, it becomes difficult to prevent \term{coercion}: the ability of some party
-to coerce (through force, payment, or otherwise) a voter to vote for a particular candidate.
+to coerce a voter to vote for a particular candidate.
 
@@
 
-Before an election is held, the body holding the election (e.g., the government) must construct four
-Tables that lie at the core of the Scantegrity system: Tables P, Q, R, and S.
+Before an election is held, the election authority must construct four Tables that lie at the core
+of the Scantegrity system: Tables P, Q, R, and S.
 
@@
 secret pseudorandom number generator key. Table P lists every ballot that will be produced for the
-election and specifies exactly what code (which we'll see later) is used for each candidate per
-ballot. These codes are generated using the pseudorandom generator and \emph{must} be kept secret.
+election and specifies exactly what code is used for each candidate per ballot. These codes are
+generated using the pseudorandom generator and \emph{must} be kept secret.
 
@@
 	\item
-		The Table R mapping is followed into Table S, and a ``check'' is added to a cell in Table R
-		(to be counted as a vote for that row's candidate).
+		The Table R mapping is followed into Table S, and a ``check'' is added to a cell in Table R,
+		to be counted as a vote for that row's candidate.
 \end{enumerate}
@@
 Helios \cite{helios} -- unlike Scantegrity and \pv{} -- is an \emph{online} voting
-system that attempts to meet many of the same goals (namely, verifiability).
+system; however, it, too, is designed with an emphasis on verifiability.
 
@@
 At the heart of Helios is a single ElGamal keypair. The secret key is known only to the Helios
-server, but the public key can (by its nature) be accessed in some way by all participants.
+server, but the public key can be accessed in some way by all participants.
 
@@
 by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
-(one which allows randomness to be specified) -- perform the encryption and SHA-1 hash him/herself
+which allows randomness to be specified -- perform the encryption and SHA-1 hash him/herself
 to verify that the hash that \emph{would} have been cast actually does represent the ballot he/she
@@
 
-The ``shuffling'' is important because it prevents an attacker (or simple onlooker) from linking
-a decrypted ballot with a particular encrypted ballot -- and thus a voter. Re-encryption means that
-an auditor examining a proof of proper decryption (see below) cannot determine how a particular
-voter cast his/her ballot by hashing all ciphertexts in the proof and matching those hashes to the
-publicly-posted encrypted vote hashes.
+The ``shuffling'' is important because it prevents an attacker from linking a decrypted ballot with
+a particular encrypted ballot -- and thus a voter. Re-encryption means that an auditor examining a
+proof of proper decryption cannot determine how a particular voter cast his/her ballot by hashing
+all ciphertexts in the proof and matching those hashes to the publicly-posted encrypted vote hashes.
 
@@
 simply decrypt encrypted votes with no attention giving to Table R. Should the mapping on
-\emph{either} size of Table R (to votes in Table Q or tallies in Table S) be deterministic, privacy
-would be compromised for half of all voters.
+\emph{either} size of Table R to votes in Table Q \emph{or} tallies in Table S be deterministic,
+privacy would be compromised for half of all voters.
 
@@
 the public implementation makes it clear to voters that they would be easy to coerce. Setting
-(physical security) aside: as with Scantegrity, Helios does not reveal to a voter all the
+physical security aside: as with Scantegrity, Helios does not reveal to a voter all the
 information necessary to \emph{prove} a decryption of his/her ballot. Though a voter is able to see
@@
 Note that each of these systems rely on publication of some information for every ballot that was
-cast (whether it be the entire encrypted ballot or a hash of the ballot).
+cast -- whether it be the entire encrypted ballot or a hash of the ballot.
 
@@
 Additionally, should this data be hidden, it could potentially be more difficult to notice ``ballot
-stuffing'' (discussed above above).
+stuffing.''
 
@@
 In each of these key systems, there exists some way to tie a vote back to a voter: there is always
-some secret. Ideally, there would be a system wherein a vote could be tallied properly (somehow)
-without being able to reveal who the vote was for. (Admittedly, that would be difficult: if that is
-the only vote, then ``tallying'' just it would reveal the candidate for which it was cast.)
+some secret. Ideally, there would be a system wherein a vote could be tallied properly without being
+able to reveal who the vote was for.
 
-But it would be a worthy goal at least to minimize (if not eliminate) the amount of data that must
-be kept secret. Usually it is one or two pieces of data -- and these systems attempt to mitigate
-risk by requiring that multiple entities (persons) be present in order to access that secret data.
+Admittedly, that would be difficult: if that is the only vote, then ``tallying'' just it would
+reveal the candidate for which it was cast. But it would be a worthy goal at least to minimize, if
+not eliminate, the amount of data that must be kept secret. Usually it is one or two pieces of data
+-- and these systems attempt to mitigate risk by requiring that multiple entities be present in
+order to access that secret data.
 
@@
 generation method to violate privacy. Helios, on the other hand, was designed with application in
-mind and therefore uses standard cryptographic techniques (e.g., ElGamal and SHA-1).
+mind and therefore uses standard cryptographic techniques (ElGamal and SHA-1).
 
@@
 and SHA-1); however, as the authors have designed the scheme with particular primitives in mind, its
-specification is less open to interpretation (and thus potentially harmful choices).
+specification is less open to interpretation and, therefore, potentially harmful choices.
 

### 2012-12-06 paper/paper.tex
Reduce parenthetical statements
Add kremer paper, "observational equivalence" privacy

@@
 
-Delaune \cite{delaune} gives several definitions of ballot secrecy.
+\cite{delaune} enumerates a hierarchy of ballot secrecy definitions.
 In order of increasing strength, they are
@@
 
-More formally, we can say that an election system has private ballots
-if a reasonably time-bounded attacker, having access to the public information
-published by the polling authority ... \todo{}
+\cite{kremer} gives an \term{observational equivalence} definition of privacy:
+An election system is private if an attacker, having access to the public
+information published by the polling authority, ``cannot distinguish
+the actual situation from one in which two voters have swapped their votes.''
+
+% For all pairs of voters $v_1$, $v_2$ ...
 

### 2012-12-06 paper/paper.tex
Describe verifiable counting in Scantegrity

@@
 
-\todo{Fill in.}
+In order to preserve ballot secrecy, it must be impossible for anyone -- including a voter
+him/herself -- to match published vote information (encrypted ballot or a hash) to its inclusion in
+the final tally, as this would reveal the candidate for which the ballot was cast. As such, these
+systems verify the accuracy of their counting indirectly by instilling in auditors confidence that
+the tallying mechanisms are correct.
+
+Scantegrity relies on unused \term{audit ballots} to prove that its Tables Q, R, and S accurately
+match ballot selections with the proper candidates. These ballots come in two forms: a group of
+ballots randomly selected and checked prior to the election by members of the election authority;
+and the collection of optional secondary ballots that are offered to voters.
+
+Auditing is then performed by revealing all bubble codes on the ballots and uncovering the entire
+R-to-S mapping in Table Q for all rows corresponding to those revealed codes. An auditor then
+manually examine the revealed information and ensure that, had a code been revealed as on a counted
+ballot, the tally would have been affected appropriately. Note that this method of verification is
+indirect in that it does not allow \emph{any} of the ballots that are cast during the election to be
+verified, for reasons previously stated. Rather, it is expected that the random selection of ballots
+beforehand, along with the selection of ballots chosen by voters as audit ballots, is a sufficient
+sample to detect improper counting. Thus, if these checks past, it is accepted that all other
+ballots must also be counted properly.
+
+It is important to note that in order for this assurance to hold, the predetermined Tables cannot be
+modified after they are initially created (prior to \emph{any} auditing). Through some means, the
+election authority must therefore \term{commit} to the predetermined tables such that any change to
+the data is either impossible or detectable.
 

### 2012-12-06 paper/paper.tex
Reference Scantegrity ballot auditing in its description

@@
 \usepackage{multicol}
-
-% don't number sections
-%\setcounter{secnumdepth}{0}
 
@@
 
+After these tables have been generated, the election authority must \term{commit} to their contents
+so that any change from this point forward is impossible or detectable.
+
+It is at this point that the election authority audits a selection of the ballots; this is discussed
+further in our analysis.
+
 \todo{Include our own depiction of the tables in an image.}
@@
 revealed, and the ballot is marked as an audit ballot. An audit ballot is scanned, but the voter is
-allowed to keep the ballot for later verification.
+allowed to keep the ballot for later verification. This verification process is described and
+discussed in our analysis.
 

### 2012-12-06 paper/paper.tex
Describe verifiable counting in Helios

@@
 
+In some ways, count verification is simpler than that in Scantegrity. We have already discussed how
+Helios uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this mechanism,
+they are decrypted, and so the actual plaintext ballots are exposed. From that point, tallying is
+straightforward.
+
 \subsection{Coercion prevention}

### 2012-12-06 paper/paper.tex
Remove superfluous "organization"
Take a stab at the conclusion

@@
 An election involves an information exchange between many independent \term{voters} and a single
-\term{election authority} organization.
+\term{election authority}.
 In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
@@
 
-\todo{Fill in.}
+These systems -- and other similar systems not examined here -- demonstrate how mathematical and
+cryptographic techniques can be used to guarantee voters that election results accurately reflect
+the votes that were cast by the electorate.
+
+Compared to traditional voting systems, each of the schemes we have examined provides voters a
+greater assurance that their votes \emph{are} counted and that the election authority has
+\emph{properly} counted all votes that were cast. By satisfying the various facets of ballot
+secrecy, they also serve to enforce practices that in general must only be assumed: that voters
+cannot be coerced and that a voter is never required to reveal the candidate for whom he/she voted.
+
+However, other potentially-important considerations, such as identity of (non-)voters, are not
+addressed by these systems at all but do lay groundwork for further research.
 

### 2012-12-06 paper/paper.tex
Rewrite discussion of secrets and trust

@@
 
-\subsection{Keeping secrets}
+\subsection{Secrets and trust}
 
-In each of these key systems, there exists some way to tie a vote back to a voter: there is always
-some secret. Ideally, there would be a system wherein a vote could be tallied properly without being
-able to reveal who the vote was for.
+In each of these key systems, there exists some way to tie a vote back to a voter or to a physical
+receipt: there is always some secret. Ideally, there would be a system wherein a vote could be
+tallied properly without \emph{anyone} being able to reveal the candidate selected on the ballot.
+Admittedly, to achieve this would be difficult: in the case of a single vote, ``tallying'' just it
+would reveal the candidate for which it was cast. But if a secret \emph{must} be kept, it is
+worthwhile to take precautions to minimize risk of compromise.
 
-Admittedly, that would be difficult: if that is the only vote, then ``tallying'' just it would
-reveal the candidate for which it was cast. But it would be a worthy goal at least to minimize, if
-not eliminate, the amount of data that must be kept secret. Usually it is one or two pieces of data
--- and these systems attempt to mitigate risk by requiring that multiple entities be present in
-order to access that secret data.
+In both Scantegrity and Helios, the most fundamental secret is a key. In Scantegrity, this is the
+seed to the pseudorandom number generator used to create Table P; and in Helios, it is a single
+ElGamal keypair used for all encryption/decryption operations during a particular election.
 
-With each of these systems, there is \emph{still} a significant level of trust placed in the body
-holding the election. This is the issue with secrets: \emph{someone} must keep them.
+The random seed in Scantegrity is a secret that is shared among a group of members of the election
+authority, thereby mitigating risk of compromise.
 
-In order for a voting system to be \emph{useful}, it must be feasible given the nature of society
-today, and so solutions that rely on, say, personally-maintained keypairs are outside the scope of
-a practical system.
+But in Helios, there is a single private ElGamal key that lives on the server. (Note that the
+creators of Helios admit this weakness but choose to overlook it, as it is their goal to make
+verifiable voting an accessible technology, even with some costs.)
 
-In the end, there are as yet no \emph{perfect} verifiable voting systems that achieve both complete
-privacy and completely verifiable integrity, as there are always attack vectors (often physical
-ones). This has not been seen as a problem by researchers in the past, as physical security is
-indeed outside the scope of these systems as they have been developed; but perhaps with further
-research into advanced cryptographic schemes we can someday eliminate any state-held secret data and
-yet hold a completely verifiable election.
+Furthermore, with each of these systems, there is \emph{still} a significant level of trust placed
+in the body holding the election. This is the issue with secrets: \emph{someone} must keep them, and
+we must place some trust in that party. In Scantegrity, for example, we must assume that we can
+trust at least enough of the secret holders so that the seed cannot be obtained and used
+inappropriately.
 
-\todo{Remark on the fact that the election itself has a single primary ElGamal keypair.}
+Public-key encryption could potentially solve some of these issues; however, it is not feasible
+today to require each voter to maintain his/her own keypair.
 

### 2012-12-06 paper/paper.tex
Rework brief section on voter involvement

@@
 
-It is important to note -- and the Helios researchers note this -- that this hinges on active
-involvement from the community.
+It is worth noting that without active participation on the part of the voters, none of these
+schemes provide significant benefit. Only if some voters actually \emph{do} audit the election
+processes is there any guarantee that the election was fair.
+
+The creators of Helios note this fact, and it is reflected in their work, as the system makes at
+least recording verification an obvious and easy process.
 

### 2012-12-06 paper/paper.tex
Add microtype package.
spelling

@@
 \usepackage{multicol}
+\usepackage{microtype}
 
@@
 an individual's ballot, then the voter's own will may be undermined by coercion.
-Therefore a voting system must maintain secrecy of invididuals' votes to avoid
+Therefore a voting system must maintain secrecy of individuals' votes to avoid
 the possibility that a voter may receive retribution or reward for casting a vote
@@
 
-At the heart of Helios is a single ElGamal keypair. The secret key is known only to the Helios
+At the heart of Helios is a single ElGamal key pair. The secret key is known only to the Helios
 server, but the public key can be accessed in some way by all participants.
@@
 seed to the pseudorandom number generator used to create Table P; and in Helios, it is a single
-ElGamal keypair used for all encryption/decryption operations during a particular election.
+ElGamal key pair used for all encryption/decryption operations during a particular election.
 
@@
 Public-key encryption could potentially solve some of these issues; however, it is not feasible
-today to require each voter to maintain his/her own keypair.
+today to require each voter to maintain his/her own key pair.
 

### 2012-12-06 paper/paper.tex
Use feminine singular pronouns.

@@
 Though ballot secrecy prevents such a party from determining that a voter has done as asked, it is a
-different problem to ensure that even the voter him/herself cannot prove that his/her ballot was
+different problem to ensure that even the voter herself cannot prove that her ballot was
 cast a certain way. We will show, in describing these systems, that the cryptographic techniques
 used to provide ballot secrecy also ensure -- in the case of in-person elections -- that a voter
-cannot prove his/her ballot was cast a certain way even with the data necessarily exposed to provide
+cannot prove her ballot was cast a certain way even with the data necessarily exposed to provide
 verifiability.
@@
 
-All candidates are listed on the optical-scan ballot, and the voter makes his/her choice by filling
+All candidates are listed on the optical-scan ballot, and the voter makes her choice by filling
 in a ``bubble'' that reveals an alphanumeric confirmation code (as specified in the private Table
 P), which the voter then records on the receipt portion. The ballot is sent through an optical
-scanner, and the voter takes his/her receipt when leaving the polling location. It can later be
+scanner, and the voter takes her receipt when leaving the polling location. It can later be
 compared against published Table Q to ensure that the vote was recorded properly.
@@
 
-When a voter goes to cast a vote, his/her candidate selection is encrypted locally (i.e., on his/her
+When a voter goes to cast a vote, her candidate selection is encrypted locally (i.e., on her
 computer terminal, in the browser) using ElGamal. Prior to casting the ballot, the voter is
-presented with a SHA-1 hash of his/her encrypted ballot. At this point, the voter may choose either
+presented with a SHA-1 hash of her encrypted ballot. At this point, the voter may choose either
 to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
@@
 by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
-which allows randomness to be specified -- perform the encryption and SHA-1 hash him/herself
+which allows randomness to be specified -- perform the encryption and SHA-1 hash herself
 to verify that the hash that \emph{would} have been cast actually does represent the ballot he/she
@@
 a particular encrypted ballot -- and thus a voter. Re-encryption means that an auditor examining a
-proof of proper decryption cannot determine how a particular voter cast his/her ballot by hashing
+proof of proper decryption cannot determine how a particular voter cast her ballot by hashing
 all ciphertexts in the proof and matching those hashes to the publicly-posted encrypted vote hashes.
@@
 
-At the time a ballot is cast, both Scantegrity and Helios attempt to ensure a voter that his/her
+At the time a ballot is cast, both Scantegrity and Helios attempt to ensure a voter that her
 vote is recorded exactly as intended.
@@
 In Scantegrity, this verification is rolled into the ballot casting process. After recording the
-receipt him/herself, a voter can visually check that the code on the receipt matches the candidates
+receipt herself, a voter can visually check that the code on the receipt matches the candidates
 selected on the ballot.
@@
 so the system cannot simply cheat and show the user a predetermined hash: it \emph{must} be a valid
-one -- otherwise the deception would be revealed should the voter choose to exercise his/her right
+one -- otherwise the deception would be revealed should the voter choose to exercise her right
 to audit.
@@
 In the case on Scantegrity, this information is primarily embodied in the published version of Table
-Q. After the election, a voter can compare his/her receipt code with that revealed for his ballot in
+Q. After the election, a voter can compare her receipt code with that revealed for his ballot in
 Table Q. If the code does not match, then something is amiss.
@@
 In order to preserve ballot secrecy, it must be impossible for anyone -- including a voter
-him/herself -- to match published vote information (encrypted ballot or a hash) to its inclusion in
+herself -- to match published vote information (encrypted ballot or a hash) to its inclusion in
 the final tally, as this would reveal the candidate for which the ballot was cast. As such, these
@@
 physical security aside: as with Scantegrity, Helios does not reveal to a voter all the
-information necessary to \emph{prove} a decryption of his/her ballot. Though a voter is able to see
+information necessary to \emph{prove} a decryption of her ballot. Though a voter is able to see
 encryption details for ballots chosen for audit, that information is never displayed to the user
@@
 Public-key encryption could potentially solve some of these issues; however, it is not feasible
-today to require each voter to maintain his/her own key pair.
+today to require each voter to maintain her own key pair.
 

### 2012-12-06 paper/paper.tex
diction

@@
   Current election processes do not allow participants to verify the accuracy of vote counting.
-  Applied cryptography research has yielded a number of candidate systems to replace or accompany
+  Applied cryptography research has yielded a number of candidate systems that replace or accompany
   existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
@@
 solutions, but their propensity to be externally observable limits the potential for widespread
-abuse.  Internal manipulation by the government conducting the poll is a more insidious threat, and
+abuse.  Internal manipulation by the authority conducting the poll is a more insidious threat, and
 it is here where we may fruitfully apply cryptography to ensure honesty. Research in this field has
-yielded a number of candidate systems to replace or accompany existing voting procedures to provide
+yielded a number of candidate systems that replace or accompany existing voting procedures to provide
 fairness guarantees while maintaining ballot secrecy.
@@
 strive to satisfy. Second, we will describe each of the three voting schemes in turn. We will then
-analyze their differing approaches to security and how well they meet the necessary goals. Finally,
+analyze their differing approaches to security and how well they achieve the desired goals. Finally,
 we will present some ideas that are not -- but perhaps should be -- considered by these schemes, and
@@
 by the election authority.
-A voter, or any other third party \term{auditor}, may also verify the accuracy of the final tallies
+A voter, or any other third party \term{auditor}, may also verify the accuracy of the final vote tallies
 reported by the election authority. \cite{preta}
-Voting is complicated by the requirement that all votes be secretive to avoid coercion.
+Voting is complicated by the requirement that all votes remain secret to avoid coercion.
 

### 2012-12-06 paper/paper.tex
Make all first-person clauses present tense.

@@
 
-In this survey, we will study three of the most well-known solutions: the in-person voting systems
+In this survey, we study three of the most well-known solutions: the in-person voting systems
 Scantegrity and \pv{} and the online voting system Helios.
 
-First, we will discuss the background of verifiable voting schemes and the security goals they
-strive to satisfy. Second, we will describe each of the three voting schemes in turn. We will then
+First, we discuss the background of verifiable voting schemes and the security goals they
+strive to satisfy. Second, we describe each of the three voting schemes in turn. We then
 analyze their differing approaches to security and how well they achieve the desired goals. Finally,
-we will present some ideas that are not -- but perhaps should be -- considered by these schemes, and
-we will draw conclusions about the role of these schemes in elections today and in the future.
+we present some ideas that are not -- but perhaps should be -- considered by these schemes, and
+we draw conclusions about the role of these schemes in elections today and in the future.
 
@@
 different problem to ensure that even the voter herself cannot prove that her ballot was
-cast a certain way. We will show, in describing these systems, that the cryptographic techniques
+cast a certain way. We show, in describing these systems, that the cryptographic techniques
 used to provide ballot secrecy also ensure -- in the case of in-person elections -- that a voter
@@
 
-This process will be discussed further in the analysis.
+We further discuss this process in our analysis.
 
@@
 
-We will analyze these voting systems by considering each security goal in turn.
+We analyze these voting systems by considering each security goal in turn.
 

### 2012-12-06 paper/paper.tex
Use feminine singular pronouns.
I previously missed instances of "he/she".

@@
 
-When casting a ballot, a voter knows which candidate(s) he/she \emph{intended} to vote for -- but
+When casting a ballot, a voter knows which candidate(s) she \emph{intended} to vote for -- but
 once the ballot is cast, a system that supports verification of vote reporting allows the voter to
-compare the recorded vote to what he/she intended to indicate on the ballot.
+compare the recorded vote to what she intended to indicate on the ballot.
 
 For example, at an in-person polling location -- ignoring ballot secrecy (see below) -- a voter
-could be shown a screen giving the name of the candidate(s) he/she just voted for. If the display
+could be shown a screen giving the name of the candidate(s) she just voted for. If the display
 does not match the voter's intention, then the voter can ``try again'' -- or call into question the
@@
 
-After a ballot has been cast, and the voter has left the polling place, how can he/she be certain
-that the ballot used in the final count is what he/she actually cast? (This could be a problem even
+After a ballot has been cast, and the voter has left the polling place, how can she be certain
+that the ballot used in the final count is what she actually cast? (This could be a problem even
 if the user has verified the \emph{recording} of the vote.)
@@
 It is possible -- as we shall see -- for a voting system to allow a voter to check that the ballot
-he/she cast is exactly what was considered during vote counting.
+she cast is exactly what was considered during vote counting.
 
@@
 to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
-complete. But when a voter chooses to ``audit,'' he/she is presented with \emph{all} of the data
+complete. But when a voter chooses to ``audit,'' she is presented with \emph{all} of the data
 used to encrypt the vote. Namely, this includes the public key and the ``randomness'' that were used
@@
 which allows randomness to be specified -- perform the encryption and SHA-1 hash herself
-to verify that the hash that \emph{would} have been cast actually does represent the ballot he/she
+to verify that the hash that \emph{would} have been cast actually does represent the ballot she
 intended to cast.
@@
 
-Helios does not actually permit a voter to verify the ballot that he/she actually casts. Rather, it
+Helios does not actually permit a voter to verify the ballot that she actually casts. Rather, it
 allows users to verify a ballot without casting it (after which point it cannot be cast without
@@
 Scantegrity prevents coercion via the manner it uses to ``encrypt'' ballots. Once cast, a ballot's
-ciphertext is \emph{always public}. A voter can claim that he/she voted in a particular manner, but
+ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
 without exposure of the data maintained in Table P -- Scantegrity's ``secret'' -- the voter has no
@@
 secrecy, they also serve to enforce practices that in general must only be assumed: that voters
-cannot be coerced and that a voter is never required to reveal the candidate for whom he/she voted.
+cannot be coerced and that a voter is never required to reveal the candidate for whom she voted.
 

### 2012-12-06 paper/paper.tex
diction. dashes.

@@
 
-The Scantegrity system \cite{scantegrity_ii} (technically, we consider an updated version known as
-Scantegrity II) is designed to provide verifiability atop existing in-person voting systems that
-rely on fill-in ballots that are processed via optical scan.
+The Scantegrity system \cite{scantegrity_ii} -- we consider an updated version technically known as
+Scantegrity II -- is designed to provide verifiability atop existing in-person voting systems that
+rely on fill-in ballots processed via optical scan.
 
@@
 
-Some selection of persons associated with the electing body use a secret-sharing scheme to protect a
+Some selection of officials conducting the election use a secret-sharing scheme to protect a
 secret pseudorandom number generator key. Table P lists every ballot that will be produced for the
@@
 
-Table R is the ``heart'' of the Scantegrity Tables: it maps cast ballots in Table Q to tally marks
+Table R comprises the heart of the Scantegrity Tables: it maps cast ballots in Table Q to tally marks
 in Table S. Each row in Table R maps a single cell in Q to a single cell in S, and the order of

### 2012-12-06 paper/paper.tex
diction

@@
 
-But in Helios, there is a single private ElGamal key that lives on the server. (Note that the
-creators of Helios admit this weakness but choose to overlook it, as it is their goal to make
-verifiable voting an accessible technology, even with some costs.)
+But in Helios, there is a single private ElGamal key that lives on the server. The
+authors of Helios acknowledge this weakness but choose to overlook it, as they aim to make
+verifiable voting an accessible technology, even with some costs.
 
-Furthermore, with each of these systems, there is \emph{still} a significant level of trust placed
+Furthermore, with each of these systems, voters must \emph{still} place a significant level of trust
 in the body holding the election. This is the issue with secrets: \emph{someone} must keep them, and

### 2012-12-07 paper/paper.tex
Literally one sentence about Pret-a-Voter.
Don't use `multicol` package
It prevents us from using the standard `figure` environment.

I got the new technique for creating a one-column abstract from:
http://www.tex.ac.uk/cgi-bin/texfaq2html?label=onecolabs.
Include mixnet depiction in paper
Remove TODO regarding an unnecessary image
Correct image path
Include Prˆet `a Voter ballot image
Figure links should go to the top of the image
Fortunately, there was an easy fix:
https://en.wikibooks.org/wiki/LaTeX/Labels_and_Cross-referencing#Pictures.
Rework discussion of Helios mixnet and decryption ver

@@
 % setup
-\documentclass[10pt]{article}
+\documentclass[10pt,twocolumn]{article}
+\usepackage{abstract}
+\usepackage[hypcap]{caption}
 \usepackage{color}
@@
 \usepackage{fullpage}
+\usepackage{graphicx}
 \usepackage{hyperref}
-\usepackage{multicol}
 \usepackage{microtype}
+\nonstopmode
 
@@
 \begin{document}
-\maketitle
-
 \thispagestyle{empty}
 
-\begin{abstract}
+\twocolumn[
+\maketitle
+\begin{onecolabstract}
 
@@
 
-\end{abstract}
-
-\begin{multicols}{2}
+\end{onecolabstract}
+]
 
@@
 
+\pv\ aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
+a fair election.
+
+\begin{figure}
+	\center
+	\includegraphics[width=0.8\columnwidth]{images/include/preta.pdf}
+	\caption{\pv{} ballot}
+	\label{fig:preta}
+\end{figure}
+
 \todo{Fill in.}
@@
 
+\begin{figure}
+	\center
+	\includegraphics[width=0.8\columnwidth]{images/include/mixnet.pdf}
+	\caption{Re-encryption \term{mixnet}}
+	\label{fig:mixnet}
+\end{figure}
+
 The ``mixnet'' accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
@@
 $c_{i}$ is then ``re-encrypted'' to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
-the random input at encrypt time been different} by a particular amount $s_{i}$.
+the random input at encrypt time been different} by a particular amount $s_{i}$. See Figure
+~\ref{fig:mixnet} for a visual depiction of this process.
 
@@
 
-Finally, votes are decrypted and tallied. At this time, Helios also publishes the information
-necessary for anyone who wishes to audit the election to verify that the mixnet's shuffling and
-decryption were performed properly.
-
-In order to provide a guarantee of proper shuffling, Helios actually shuffles the votes multiple
+In order to provide a guarantee of proper shuffling, Helios shuffles the votes multiple
 times, actually using only the final shuffle in tallying the results. The other shuffles are
@@
 other bit value indicating that it must provide a mapping from one shadow mix to another. This is
-known as an ``Honest-Verifier Zero-Knowledge'' proof, for which the probability that the final
-product is correct is equal to $1 - 2^{t}$, where $t$ is the number of shadow mixes produced.
+known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
+obtain the set of challenges allows this process to be completed entirely within the Helios system
+-- without human involvement -- for publication and auditor verification.
 
-Similarly, the Chaum-Peterson zero-knowledge proof technique is used to prove that decryption is
-correct. \todo{How much detail should we provide?}
+Once auditors are satisfied with the proofs, Helios decrypts and tallies the ballots. Similarly,
+Helios proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
+known as the \term{Chaum-Pedersen protocol}, through which the system proves that \emph{all}
+decrypted ballots are in fact correct plaintexts for the corresponding mixnet outputs. Challenges
+are generated by the system using a technique similar to that employed to provide mixnet proofs.
+
+At that point, the election is complete and can be verified completely by any interested party.
 
@@
 Table system.
-
-\todo{Include image showing difference between Scantegrity and Helios voting mappings.}
 
@@
 
-\end{multicols}
-
 \end{document}

### 2012-12-07 paper/paper.tex
Add TODO regarding coverage of attacks
Increase image size
Add an em of space after the abstract.
Pret-a-voter beginnings.

@@
 	use cryptographic techniques to meet those goals.
-
+    \vspace{1em}
 \end{onecolabstract}
@@
 
-\pv\ aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
+\pv\ also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
 a fair election.
+
+\subsection{Before voting}
+
+The paper ballot form in \pv\ consists of two separable sides.
+The left-hand side lists the candidates in permuted order.
+A mark on the right-hand side in an initially empty slot adjacent to a candidate indicates a vote for that candidate.
+In addition to the recorded vote, the right-hand side also includes the so-called ``onion'', an encryption of the ballot's particular candidate permutation.
+See Figure \ref{fig:preta} for a depiction of the ballot form.
 
@@
 	\center
-	\includegraphics[width=0.8\columnwidth]{images/include/preta.pdf}
+	\includegraphics[width=\columnwidth]{images/include/preta.pdf}
 	\caption{\pv{} ballot}
@@
 \end{figure}
+
+\todo{Discuss variants (decryption mixnets, reencryption mixnets) on how to generate the encrypted permutations.}
+
+\subsection{Voting}
+
+Upon arriving at the polling place, a voter receives one or more ballots.
+She chooses one of her ballots forms at random and privately marks her vote on the right-hand side.
+She detaches her cast vote from the corresponding candidate list on the left-hand side, which is subsequently destroyed.
+Her cast vote is scanned into and recorded by the system, which prints a digital signature on the now recorded ballot to constitute a receipt.
+The voter retains this receipt to later verify that her vote appears correctly in the tally.
+
+The voter can optionally request an audit of her other ballot(s) to test that the decrypted onion on the right-hand side in fact corresponds to the ordering of candidates printed on the left-hand side.
+Once audited, a ballot can no longer be cast.
+Independent auditing authorities may also randomly choose uncast ballots to audit throughout the election process to provide further assurance.
+
+\subsection{After voting}
+A publicly-available bulletin board publishes all recorded votes, i.e., the right-hand sides of each cast ballot, including its onion and vote as recorded.
+A voter can then verify that her vote was correctly recorded by checking that her receipt matches the information displayed on the bulletin board.
+
+\todo{Tallying the vote}
 
@@
 
+\todo{How much should we discuss here? What I said is very incomplete, but the Scantegrity II paper
+doesn't say much more on the subject (instead deferring to other readings).}
+
 \subsection{Voter involvement}

### 2012-12-07 paper/paper.tex
More pret-a

@@
 Upon arriving at the polling place, a voter receives one or more ballots.
-She chooses one of her ballots forms at random and privately marks her vote on the right-hand side.
+She chooses one of her ballot forms at random and privately marks her vote on the right-hand side.
 She detaches her cast vote from the corresponding candidate list on the left-hand side, which is subsequently destroyed.
@@
 
-The voter can optionally request an audit of her other ballot(s) to test that the decrypted onion on the right-hand side in fact corresponds to the ordering of candidates printed on the left-hand side.
+The voter can optionally request an audit of her other, unused ballots to test that the decrypted onion on the right-hand side in fact corresponds to the ordering of candidates printed on the left-hand side.
+Since she arbitrarily chose which ballot to actually cast, this process offers assurance that it too is correct.
 Once audited, a ballot can no longer be cast.

### 2012-12-07 paper/paper.tex
Mention Condorcet and STV.

@@
 
-\pv\ also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
+\pv\ \cite{preta} also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
 a fair election.
@@
 See Figure \ref{fig:preta} for a depiction of the ballot form.
+
+Note that this ballot form supports alternative voting methods, such as Condorcet and Single Transferable Vote, in which voters rank candidates in order of preference rather than voting for a single candidate.
 

### 2012-12-07 paper/paper.tex
line breaks
Finished the section on secrecy

@@
 \usepackage{microtype}
+\usepackage{amsmath}
 \nonstopmode
@@
 \newcommand{\pv}{\preta{} Voter}
+\newcommand{\abs}[1]{\ensuremath{\left\vert#1\right\vert}}
 
@@
 \term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.
+Countries such as the United States hold voting privacy as a fundamental right,
+and under traditional voting systems, privacy implies coercion resistance.
+For more complicated systems, however, we will need to explicitly discuss
+stronger formalizations of coercibility.
 
@@
 
+A tempting notion of privacy would be to suggestion that it ought to be impossible
+to determine any fact about a voter's vote. As \cite{preta} notes, however,
+this is impossible to achieve, as demonstrated by the case of a unanimous election,
+in which case every vote is trivially known.
 \cite{kremer} gives an \term{observational equivalence} definition of privacy:
@@
 the actual situation from one in which two voters have swapped their votes.''
+This notion is formalized using a process calculus such as the pi calculus.
 
-% For all pairs of voters $v_1$, $v_2$ ...
+Another intuition which we will find useful in discussion of the Scantegrity II system is:
+Assume a list of votes $a_1, a_1, \ldots, a_n$ is public, and the mapping between
+voters and votes is described by a secret permutation $\pi_k$ such that the vote
+belonging to voter $v_i$ is $a_{\pi_k(i)}$.
+As long as an attacker cannot gain information about $\pi_k$,
+the system reveals no more information than is implies by an anonymized list of votes.
+
+Note that privacy does not necessarily imply that votes are hidden from the election
+authority. In some developing states where corruption is prevalent, this may be desirable,
+again for the purpose of limiting coercibility.
+This requirement is significantly more restrictive, however, and is not addressed by
+any systems under our discussion.
 
@@
 
-\subsection{Coercion resistance}
-
-\subsection{Stuff that will be moved into one of the previous sections}
-
-Countries such as the United States hold as a fundamental right that voting can be performed
-in secret to reduce the possibility of voter coercion from any private entities.
-In some developing states where corruption is prevalent, it may be desirable keep an
-individual's vote hidden even from the election authority, again for the reason of
-limiting coercibility. The latter goal is significantly more restrictive.
-
-Ballot secrecy, often referred to as \term{receipt-freeness}, is perhaps the most complicated
-security goal to address in a verifiable voting system.
+With conventional in-person voting, privacy provided by physical security imposed
+at polling locations is sufficient to ensure secrecy.
+A party who cannot \emph{watch} a voter cast a ballot and cannot know what vote
+was cast, because traditional systems have no need to retain any information
+beyond the vote itself.
+Receipt-freeness, however, is a complication added by verifiable voting system.
 Secrecy and verifiability are naturally at odds, and only through cryptography can we
@@
 
-Amidst these other goals, it becomes difficult to prevent \term{coercion}: the ability of some party
-to coerce a voter to vote for a particular candidate.
+Receipt-freeness implies that even if a voter wants to tell a coercer that
+she has cast a particular vote, she is necessarily unable to prove it.
 
-With conventional in-person voting, coercion is thwarted to some extent by the physical security
-imposed at polling locations: a party cannot \emph{watch} a voter cast a ballot and so cannot rest
-assured that the voter did as told.
+\subsection{Coercion resistance}
 
-Though ballot secrecy prevents such a party from determining that a voter has done as asked, it is a
-different problem to ensure that even the voter herself cannot prove that her ballot was
-cast a certain way. We show, in describing these systems, that the cryptographic techniques
-used to provide ballot secrecy also ensure -- in the case of in-person elections -- that a voter
-cannot prove her ballot was cast a certain way even with the data necessarily exposed to provide
-verifiability.
+Coercion resistance means that secrecy is maintained even if interaction
+with the coercer is allowed throughout the voting process.
+The distinction between receipt-freeness and coercion resistance is subtle,
+and is commonly often lost in ambiguity due to a lack of formal definitions. \cite{delaune}
+In some verifiable voting systems, receipt-freeness directly implies coercion resistance,
+but this is not necessarily the case.
+
+Even in a receipt-free system,
+if the voting process involves a multi-step iteraction involving the coercer,
+it may be possible for the voter to prove to the coercer that she is following
+some protocol. \cite{delaune}
+A simple example that is common to many proposed voting systems is
+the \term{Italian attack}. \cite{preta}
+This problem arises when the ballot contains a large number of voting options,
+such as a ranked election in which the number of possibilities grows as the
+factorial of the number of candidates.
+If the voter and coercer have one interaction prior to voting,
+they can follow this protocol:
+\begin{enumerate}
+\item A coercer who favors candidate $c_1$ randomly permutes $[2, n]$ and
+communicates the resulting permutation $\pi$ to the voter.
+\item The voter casts a ballot ranking candidates in the order
+$c_1, c_{\pi(2)}, c_{\pi(3)}, \ldots$.
+\item The coercer, seeing the resulting ballot in the published list of votes,
+is assured that it was cast by the voter with probability
+$\ge 1 - \frac{1}{(n-1)!}$.
+\end{enumerate}
 

### 2012-12-07 paper/paper.tex
Add note about random candidate ordering providing voter privacy.
Add scantegrity image

@@
 
-\todo{Include our own depiction of the tables in an image.}
+\begin{figure}
+	\center
+	\includegraphics[width=\columnwidth]{images/include/scantegrity.pdf}
+	\caption{
+		Visualization of links between Scantegrity tables.
+		Lines represent pointers in Table R.
+		Dashed lines represent secret (unpublished) values.
+	}
+	\label{fig:scantegrity}
+\end{figure}
 
@@
 
-Note that this ballot form supports alternative voting methods, such as Condorcet and Single Transferable Vote, in which voters rank candidates in order of preference rather than voting for a single candidate.
-
 \begin{figure}
@@
 
-\todo{Discuss variants (decryption mixnets, reencryption mixnets) on how to generate the encrypted permutations.}
+Note that this ballot form supports alternative voting methods, such as Condorcet and Single Transferable Vote, in which voters rank candidates in order of preference rather than voting for a single candidate.
+
+Presenting candidates in a different, random order on each ballot conceals the voter's choice of candidates, as long as the process of decrypting the vote hides the correlation between ballot and voter (see below).
+
+\todo{Discuss variants (decryption mixnets, reencryption mixnets) on how to generate the encrypted permutations ?????}
 
@@
 
-\todo{Tallying the vote}
+Once all votes have been cast and recorded, the election authority mixes, decrypts, and tallies the votes to determine the winners while maintaining ballot secrecy.
+Mixing the encrypted votes before or during the decryption process (depending on the \pv\ variant) ensures the votes remain anonymous, even to the officials performing the encryption, by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.
 
-\todo{Fill in.}
+\pv\ accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
+Scratch \& Vote \cite{scratch}, a variation on \pv, tallies the votes homomorphically rather than with a mixnet.
 
@@
 
-Scantegrity relies on unused \term{audit ballots} to prove that its Tables Q, R, and S accurately
-match ballot selections with the proper candidates. These ballots come in two forms: a group of
-ballots randomly selected and checked prior to the election by members of the election authority;
-and the collection of optional secondary ballots that are offered to voters.
+One source of vote auditing in Scantegrity relies on unused \term{audit ballots} to prove that its
+Tables Q, R, and S accurately match ballot selections with the proper candidates. These ballots come
+in two forms: a group of ballots randomly selected and checked prior to the election by members of
+the election authority; and the collection of optional secondary ballots that are offered to voters.
 
-Auditing is then performed by revealing all bubble codes on the ballots and uncovering the entire
-R-to-S mapping in Table Q for all rows corresponding to those revealed codes. An auditor then
-manually examine the revealed information and ensure that, had a code been revealed as on a counted
-ballot, the tally would have been affected appropriately. Note that this method of verification is
-indirect in that it does not allow \emph{any} of the ballots that are cast during the election to be
-verified, for reasons previously stated. Rather, it is expected that the random selection of ballots
-beforehand, along with the selection of ballots chosen by voters as audit ballots, is a sufficient
-sample to detect improper counting. Thus, if these checks past, it is accepted that all other
-ballots must also be counted properly.
+This auditing is then performed by revealing all bubble codes on those audit ballots and uncovering the
+entire R-to-S mapping in Table Q for all rows corresponding to those revealed codes. An auditor then
+manually examines the revealed information to ensure that, had a code been revealed as on a counted
+ballot, the tally would have been affected appropriately.
+
+Secondly, recall that for each row in Table R that does not represent an audit ballot, only half of
+the Q-to-S mapping is revealed; \emph{which} half is uncovered is chosen randomly. This prevents an
+auditor from mapping any cast ballot to its chosen candidate, but it permits \emph{partial}
+verification by allowing an observer to note that the following are true:
+\begin{itemize}
+	\item
+		If a row in Table R is \textbf{checked} and its mapping to Table Q is revealed, then the
+		corresponding cell in Table Q has a \textbf{revealed} confirmation code (indicating that the
+		code was revealed on a ballot).
+	\item
+		If a row in Table R is \textbf{unchecked} and its mapping to Table Q is revealed, then the
+		corresponding cell in Table Q has a \textbf{hidden} confirmation code (indicating that the code
+		was \emph{not} revealed on a ballot).
+	\item
+		If a row in Table R is \textbf{checked} and its mapping to Table S is revealed, then the
+		corresponding cell in Table S is \textbf{checked} (indicating an addition to a candidate's
+		tally).
+	\item
+		If a row in Table R is \textbf{unchecked} and its mapping to Table S is revealed, then the
+		corresponding cell in Table S is \textbf{unchecked} (indicating \emph{no} addition to a
+		candidate's tally).
+\end{itemize}
+This technique -- verifying a random partial sample of the data -- is called \term{random partial
+checking}. If these checks past, it is accepted that all other ballots must also be counted properly.
 
@@
 
-In some ways, count verification is simpler than that in Scantegrity. We have already discussed how
-Helios uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this mechanism,
-they are decrypted, and so the actual plaintext ballots are exposed. From that point, tallying is
-straightforward.
+In some ways, Helios count verification is simpler than that in Scantegrity. We have already
+discussed how Helios uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this
+mechanism, they are decrypted, and so the actual plaintext ballots are exposed. From that point,
+tallying is straightforward.
 

### 2012-12-07 paper/paper.tex
Correct discussion of verifiable counting in Scantegrity
remove "so-called"

--- 2012-12-07 paper/paper.tex
@@
 \begin{onecolabstract}
-
+  \begin{quote}\begin{quote}\begin{quote}
   Current election processes do not allow participants to verify the accuracy of vote counting.
@@
 	use cryptographic techniques to meet those goals.
+	\end{quote}\end{quote}\end{quote}
   \vspace{1em}
@@
 A mark on the right-hand side in an initially empty slot adjacent to a candidate indicates a vote for that candidate.
-In addition to the recorded vote, the right-hand side also includes the so-called ``onion'', an encryption of the ballot's particular candidate permutation.
+In addition to the recorded vote, the right-hand side also includes the \term{onion}, an encryption of the ballot's particular candidate permutation.
 See Figure \ref{fig:preta} for a depiction of the ballot form.

### 2012-12-07 paper/paper.tex
Ditch incomplete discussion of attacks

@@
 Before an election is held, the election authority must construct four Tables that lie at the core
-of the Scantegrity system: Tables P, Q, R, and S.
+of the Scantegrity system: Tables P, Q, R, and S (see ~\ref{fig:scantegrity}).
 
@@
 
-\subsection{Clever attacks on verifiable voting systems}
-
-Scantegrity \emph{II} claims to solve some issues with other/previous systems:
-\begin{itemize}
-	\item
-		\term{Pattern voting} and
-	\item
-		\term{Randomization attacks}, whereby it's possible to tell whether a ballot is actually random
-		or is ``biased.''
-\end{itemize}
-
-\todo{How much should we discuss here? What I said is very incomplete, but the Scantegrity II paper
-doesn't say much more on the subject (instead deferring to other readings).}
-
 \subsection{Voter involvement}

### 2012-12-07 paper/paper.tex
Remove a TODO

@@
 Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
-``mixnet.'' \todo{We should discuss re-encryption details, which are covered in the Helios paper.
-Maybe we cover the details in the \pv{} Voter discussion?}
+``mixnet.''
 

### 2012-12-07 paper/paper.tex
Say "Figure"

@@
 Before an election is held, the election authority must construct four Tables that lie at the core
-of the Scantegrity system: Tables P, Q, R, and S (see ~\ref{fig:scantegrity}).
+of the Scantegrity system: Tables P, Q, R, and S (see Figure ~\ref{fig:scantegrity}).
 

### 2012-12-07 paper/paper.tex
fix coercion resistance crap

@@
 The distinction between receipt-freeness and coercion resistance is subtle,
-and is commonly often lost in ambiguity due to a lack of formal definitions. \cite{delaune}
+and is commonly often lost in ambiguity due to a lack of formal definitions \cite{delaune}.
 In some verifiable voting systems, receipt-freeness directly implies coercion resistance,
@@
 it may be possible for the voter to prove to the coercer that she is following
-some protocol. \cite{delaune}
+some protocol \cite{delaune}.
 A simple example that is common to many proposed voting systems is
-the \term{Italian attack}. \cite{preta}
+the \term{Italian attack} \cite{preta}.
 This problem arises when the ballot contains a large number of voting options,
@@
 is assured that it was cast by the voter with probability
-$\ge 1 - \frac{1}{(n-1)!}$.
+$\ge 1 - \frac{v}{(n-1)!}$, where $v$ is the number of voters.
 \end{enumerate}

### 2012-12-07 paper/paper.tex
Improve caption on Helios mixnet depiction
more pret-a

@@
 
-\todo{Discuss variants (decryption mixnets, reencryption mixnets) on how to generate the encrypted permutations ?????}
-
 \subsection{Voting}
@@
 \pv\ accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
+\pv\ is flexible enough to use either a decryption or reencryption mixnet, and with the latter, a variety of encryption schemes.
 Scratch \& Vote \cite{scratch}, a variation on \pv, tallies the votes homomorphically rather than with a mixnet.
@@
 	\includegraphics[width=0.8\columnwidth]{images/include/mixnet.pdf}
-	\caption{Re-encryption \term{mixnet}}
+	\caption{Simple re-encryption \term{mixnet} like the one used in Helios}
 	\label{fig:mixnet}

### 2012-12-07 paper/paper.tex
Fix a typo

@@
 Even in a receipt-free system,
-if the voting process involves a multi-step iteraction involving the coercer,
+if the voting process involves a multi-step interaction involving the coercer,
 it may be possible for the voter to prove to the coercer that she is following

### 2012-12-07 paper/paper.tex
Fix term ("randomized" instead of "random")
Attack on quotation marks

@@
   existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
-	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
-	how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
+	detail security properties necessary to make an election both \term{verifiable} and \term{secret}
+	and analyze how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
 	use cryptographic techniques to meet those goals.
@@
 could be shown a screen giving the name of the candidate(s) she just voted for. If the display
-does not match the voter's intention, then the voter can ``try again'' -- or call into question the
+does not match the voter's intention, then the voter can try again -- or call into question the
 entire vote collection process.
@@
 Table S contains final vote tallies. Each column represents a particular candidate, and there will
-be one ``checked'' cell in each column for each ballot cast for that candidate.
+be one marked cell in each column for each ballot cast for that candidate.
 
@@
 All candidates are listed on the optical-scan ballot, and the voter makes her choice by filling
-in a ``bubble'' that reveals an alphanumeric confirmation code (as specified in the private Table
+in a bubble that reveals an alphanumeric confirmation code (as specified in the private Table
 P), which the voter then records on the receipt portion. The ballot is sent through an optical
@@
 
-Additionally, during the voting process, a voter can ask a poll worker for an second ``audit''
+Additionally, during the voting process, a voter can ask a poll worker for an second \term{audit}
 ballot. This ballot is initially just like any other ballot: however, \emph{all} candidate codes are
@@
 	\item
-		A ``check'' is placed on the row in Table R that maps the revealed Q value to some value in S.
+		A check mark is placed on the row in Table R that maps the revealed Q value to some value in S.
 	\item
-		The Table R mapping is followed into Table S, and a ``check'' is added to a cell in Table R,
+		The Table R mapping is followed into Table S, and a check mark is added to a cell in Table R,
 		to be counted as a vote for that row's candidate.
@@
 presented with a SHA-1 hash of her encrypted ballot. At this point, the voter may choose either
-to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
-complete. But when a voter chooses to ``audit,'' she is presented with \emph{all} of the data
-used to encrypt the vote. Namely, this includes the public key and the ``randomness'' that were used
+to submit the ballot or to audit it. In the former case, the ballot is cast and voting is
+complete. But when a voter chooses to audit, she is presented with \emph{all} of the data
+used to encrypt the vote. Namely, this includes the public key and the randomness that were used
 by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
@@
 Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
-``mixnet.''
+\term{mixnet}.
 
@@
 
-The ``mixnet'' accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
+The mixnet accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
 same key, but with different random inputs). A random permutation -- referred to as $\pi_{N}$ (where
 $N$ is the total number of votes) -- is first used to perform the shuffle. Each ciphertext
-$c_{i}$ is then ``re-encrypted'' to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
+$c_{i}$ is then \term{re-encrypted} to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
 the random input at encrypt time been different} by a particular amount $s_{i}$. See Figure
@@
 
-The ``shuffling'' is important because it prevents an attacker from linking a decrypted ballot with
+The \term{shuffling} is important because it prevents an attacker from linking a decrypted ballot with
 a particular encrypted ballot -- and thus a voter. Re-encryption means that an auditor examining a
@@
 In order to provide a guarantee of proper shuffling, Helios shuffles the votes multiple
-times, actually using only the final shuffle in tallying the results. The other shuffles are
-referred to as ``shadow mixes'' and are made public. Those mixes are hashed to obtain a bit string
+times, actually using only the final shuffle in tallying the results. The other shuffles,
+referred to as ``shadow mixes'', are made public. Those mixes are hashed to obtain a bit string
 that is used, bit-for-bit, as a set of challenges, with one bit value indicating that Helios must
@@
 	\item
-		``Mix'' the ballots in some way.
+		Mix the ballots in some way.
 	\item
@@
 
-In Scantegrity, ``public'' version of a ballot is really just an encryption of the voter's
+In Scantegrity, public version of a ballot is really just an encryption of the voter's
 selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
-particular candidate for that ballot. Table P defines an explicit, ``keyless'' encryption
+particular candidate for that ballot. Table P defines an explicit, keyless encryption
 function -- and each ballot holds just enough information from Table P to encrypt a single voter's
@@
 
-In Helios, the ``public'' ballot is a hash of an encryption. Helios uses ElGamal to encrypt ballots,
+In Helios, the public ballot is a hash of an encryption. Helios uses ElGamal to encrypt ballots,
 which -- unlike Scantegrity's core \emph{random} Table P -- could be subject to attack, given that
@@
 
-Essentially, both Scantegrity and Helios use some mechanism to ``shuffle'' votes so that -- even
+Essentially, both Scantegrity and Helios use some mechanism to shuffle votes so that -- even
 with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
@@
 
-In Scantegrity, the ballot ``mix'' is predetermined, as it is defined by the generation of Table R.
+In Scantegrity, the ballot mix is predetermined, as it is defined by the generation of Table R.
 When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
@@
 
-A common theme in verifiable voting systems seems to be the presence of a published ``bulletin
-board'' of votes. (Note that because these boards contain only encrypted information, they do not
-violate ballot secrecy.)
+A common theme in verifiable voting systems seems to be the presence of a published \term{bulletin
+board} of votes. Note that because these boards contain only encrypted information, they do not
+violate ballot secrecy.
 
@@
 \end{itemize}
-This technique -- verifying a random partial sample of the data -- is called \term{random partial
+This technique -- verifying a random partial sample of the data -- is called \term{randomized partial
 checking}. If these checks past, it is accepted that all other ballots must also be counted properly.
@@
 
-Scantegrity prevents coercion via the manner it uses to ``encrypt'' ballots. Once cast, a ballot's
+Scantegrity prevents coercion via the manner it uses to encrypt ballots. Once cast, a ballot's
 ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
-without exposure of the data maintained in Table P -- Scantegrity's ``secret'' -- the voter has no
+without exposure of the data maintained in Table P -- Scantegrity's secret -- the voter has no
 way to prove to a third party that the claim is true.
@@
 An important point regarding Scantegrity is that it also relies on a \emph{physical property} -- the
-invisible ink used when printing confirmation code ``bubbles'' -- to combat vote coercion (i.e., no
+invisible ink used when printing confirmation code bubbles -- to combat vote coercion (i.e., no
 one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
@@
 unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
-data) that would produce the same hash but for a different candidate, thus ``proving'' something
-untrue to the coercing party. (This is one reason that it is important for the system to use a
-collision-resistant hash function.)
+data) that would produce the same hash but for a different candidate, thus convincing the coercer
+of something untrue.
+This is one reason that it is important for the system to use a collision-resistant hash function.
 
@@
 
-The public nature of this information can combat ``ballot stuffing.'' If names are associated with
+The public nature of this information can combat ballot stuffing. If names are associated with
 the posted ballots, then it should be obvious to one or more careful observers (given sufficient
 resources) that nonexistent persons are being posted. Furthermore, publication of ballots
-per-precinct can reveal ``stuffing'' should the number of ballots being reported by a particular
+per-precinct can reveal stuffing should the number of ballots being reported by a particular
 precinct/polling location be significantly higher than expected \cite{helios}.
@@
 One might wish to prevent a party from determining who did or did not cast \emph{any} ballot.
-As we've seen, \term{verifiable counting} typically relies on the ``public'' nature of this data.
-Additionally, should this data be hidden, it could potentially be more difficult to notice ``ballot
-stuffing.''
+As we've seen, \term{verifiable counting} typically relies on the public nature of this data.
+Additionally, should this data be hidden, it could potentially be more difficult to notice ballot
+stuffing.
 
@@
 tallied properly without \emph{anyone} being able to reveal the candidate selected on the ballot.
-Admittedly, to achieve this would be difficult: in the case of a single vote, ``tallying'' just it
+Admittedly, to achieve this would be difficult: in the case of a single vote, tallying only that vote
 would reveal the candidate for which it was cast. But if a secret \emph{must} be kept, it is

### 2012-12-07 paper/paper.tex
Clarify statements about Helios mixing

@@
 tracing a vote to its decryption. Unlike in Scantegrity, \emph{all} encrypted votes can be traced to
-their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally.
+their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
+those one cannot connect those two traces, such that secrecy is preserved.
 

### 2012-12-07 paper/paper.tex
Italicize system names

--- 2012-12-07 paper/paper.tex
@@
 	detail security properties necessary to make an election both \term{verifiable} and \term{secret}
-	and analyze how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
+	and analyze how three popular verifiable voting systems
+	-- \term{Scantegrity}, \term{\pv{}}, and \term{Helios} --
 	use cryptographic techniques to meet those goals.
@@
 In this survey, we study three of the most well-known solutions: the in-person voting systems
-Scantegrity and \pv{} and the online voting system Helios.
+\term{Scantegrity} and \term{\pv{}} and the online voting system \term{Helios}.
 
@@
 
-Another intuition which we will find useful in discussion of the Scantegrity II system is:
+Another intuition which we will find useful in discussion of the \term{Scantegrity} system is:
 Assume a list of votes $a_1, a_1, \ldots, a_n$ is public, and the mapping between
@@
 
-\section{Scantegrity}
+\section{\term{Scantegrity}}
 
-The Scantegrity system \cite{scantegrity_ii} -- we consider an updated version technically known as
-Scantegrity II -- is designed to provide verifiability atop existing in-person voting systems that
+The \term{Scantegrity} system \cite{scantegrity_ii}
+-- we consider an updated version technically known as \term{Scantegrity II} --
+is designed to provide verifiability atop existing in-person voting systems that
 rely on fill-in ballots processed via optical scan.
@@
 Before an election is held, the election authority must construct four Tables that lie at the core
-of the Scantegrity system: Tables P, Q, R, and S (see Figure ~\ref{fig:scantegrity}).
+of the \term{Scantegrity} system: Tables P, Q, R, and S (see Figure ~\ref{fig:scantegrity}).
 
@@
 
-Table R comprises the heart of the Scantegrity Tables: it maps cast ballots in Table Q to tally marks
+Table R comprises the heart of the \term{Scantegrity} tables: it maps cast ballots in Table Q to tally marks
 in Table S. Each row in Table R maps a single cell in Q to a single cell in S, and the order of
@@
 	\caption{
-		Visualization of links between Scantegrity tables.
+		Visualization of links between \term{Scantegrity} tables.
 		Lines represent pointers in Table R.
@@
 
-A Scantegrity ballot consists of two portions: a special optical-scan ballot strip and a second
+A \term{Scantegrity} ballot consists of two portions: a special optical-scan ballot strip and a second
 piece of paper that the voter will keep as a receipt. Each ballot is identified by a unique number,
@@
 
-\section{\pv{}}
+\section{\term{\pv{}}}
 
@@
 	\includegraphics[width=\columnwidth]{images/include/preta.pdf}
-	\caption{\pv{} ballot}
+	\caption{\term{\pv{}} ballot}
 	\label{fig:preta}
@@
 
-\section{Helios}
+\section{\term{Helios}}
 
-Helios \cite{helios} -- unlike Scantegrity and \pv{} -- is an \emph{online} voting
+\term{Helios} \cite{helios} -- unlike \term{Scantegrity} and \term{\pv{}} -- is an \emph{online} voting
 system; however, it, too, is designed with an emphasis on verifiability.
@@
 
-At the heart of Helios is a single ElGamal key pair. The secret key is known only to the Helios
+At the heart of \term{Helios} is a single ElGamal key pair. The secret key is known only to the \term{Helios}
 server, but the public key can be accessed in some way by all participants.
@@
 
-Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
+Once all ballots have been collected by the \term{Helios} server, they are shuffled by a cryptographic
 \term{mixnet}.
@@
 	\includegraphics[width=0.8\columnwidth]{images/include/mixnet.pdf}
-	\caption{Simple re-encryption \term{mixnet} like the one used in Helios}
+	\caption{Simple re-encryption \term{mixnet} like the one used in \term{Helios}}
 	\label{fig:mixnet}
@@
 
-In order to provide a guarantee of proper shuffling, Helios shuffles the votes multiple
+In order to provide a guarantee of proper shuffling, \term{Helios} shuffles the votes multiple
 times, actually using only the final shuffle in tallying the results. The other shuffles,
 referred to as ``shadow mixes'', are made public. Those mixes are hashed to obtain a bit string
-that is used, bit-for-bit, as a set of challenges, with one bit value indicating that Helios must
+that is used, bit-for-bit, as a set of challenges, with one bit value indicating that \term{Helios} must
 provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
@@
 known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
-obtain the set of challenges allows this process to be completed entirely within the Helios system
+obtain the set of challenges allows this process to be completed entirely within the \term{Helios} system
 -- without human involvement -- for publication and auditor verification.
 
-Once auditors are satisfied with the proofs, Helios decrypts and tallies the ballots. Similarly,
-Helios proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
+Once auditors are satisfied with the proofs, \term{Helios} decrypts and tallies the ballots. Similarly,
+\term{Helios} proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
 known as the \term{Chaum-Pedersen protocol}, through which the system proves that \emph{all}
@@
 
-In both Scantegrity and Helios, the following information is revealed after the election:
+In both \term{Scantegrity} and \term{Helios}, the following information is revealed after the election:
 \begin{itemize}
@@
 
-In Scantegrity, public version of a ballot is really just an encryption of the voter's
+In \term{Scantegrity}, public version of a ballot is really just an encryption of the voter's
 selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
@@
 
-In Helios, the public ballot is a hash of an encryption. Helios uses ElGamal to encrypt ballots,
-which -- unlike Scantegrity's core \emph{random} Table P -- could be subject to attack, given that
-ElGamal is a published encryption function. Similarly, Helios uses the standard SHA-1 hash algorithm
-to hash encrypted ballots. Note that we are not making a precise quantification about Helios's
+In \term{Helios}, the public ballot is a hash of an encryption. \term{Helios} uses ElGamal to encrypt ballots,
+which -- unlike \term{Scantegrity}'s core \emph{random} Table P -- could be subject to attack, given that
+ElGamal is a published encryption function. Similarly, \term{Helios} uses the standard SHA-1 hash algorithm
+to hash encrypted ballots. Note that we are not making a precise quantification about \term{Helios}'s
 security: rather, we simply note that the difference between these two systems can be thought of as
-a tradeoff between key size and privacy guarantees. Scantegrity essentially has an immensely large
+a tradeoff between key size and privacy guarantees. \term{Scantegrity} essentially has an immensely large
 key that -- because it is theoretically completely random -- ensures that ciphertext cannot be
-decrypted. Helios, however, uses known algorithms with shorter keys that could potentially be
+decrypted. \term{Helios}, however, uses known algorithms with shorter keys that could potentially be
 attacked. Compromise of keys in either system would destroy their privacy guarantees.
@@
 
-Essentially, both Scantegrity and Helios use some mechanism to shuffle votes so that -- even
+Essentially, both \term{Scantegrity} and \term{Helios} use some mechanism to shuffle votes so that -- even
 with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
@@
 
-In Scantegrity, the ballot mix is predetermined, as it is defined by the generation of Table R.
+In \term{Scantegrity}, the ballot mix is predetermined, as it is defined by the generation of Table R.
 When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
@@
 
-Where Table R lies between encryptions and decryptions in Scantegrity, Helios makes use of a
+Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{Helios} makes use of a
 cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
-tracing a vote to its decryption. Unlike in Scantegrity, \emph{all} encrypted votes can be traced to
-their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally.
+tracing a vote to its decryption. Unlike in \term{Scantegrity}, \emph{all} encrypted votes can be traced to
+their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
+those one cannot connect those two traces, such that secrecy is preserved.
 
 At a high level, the difference between these two schemes is in the number of mappings that must be
-kept secret in order to ensure ballot secrecy. In Scantegrity, Table R has one mapping to Table Q
+kept secret in order to ensure ballot secrecy. In \term{Scantegrity}, Table R has one mapping to Table Q
 and a second to Table S, and neither of these can be compromised to ensure secrecy for all ballots.
-But in Helios, use of a cryptographic mixnet means that both inputs and outputs can be mapped to
-voters and tallies, respectively, without revealing the inner mapping. In some ways, Helios's
-approach accomplishes the same goals as \emph{but} is implemented as an antithesis of Scantegrity's
+But in \term{Helios}, use of a cryptographic mixnet means that both inputs and outputs can be mapped to
+voters and tallies, respectively, without revealing the inner mapping. In some ways, \term{Helios}'s
+approach accomplishes the same goals as \emph{but} is implemented as an antithesis of \term{Scantegrity}'s
 Table system.
@@
 
-At the time a ballot is cast, both Scantegrity and Helios attempt to ensure a voter that her
+At the time a ballot is cast, both \term{Scantegrity} and \term{Helios} attempt to ensure a voter that her
 vote is recorded exactly as intended.
 
-In Scantegrity, this verification is rolled into the ballot casting process. After recording the
+In \term{Scantegrity}, this verification is rolled into the ballot casting process. After recording the
 receipt herself, a voter can visually check that the code on the receipt matches the candidates
@@
 
-Helios does not actually permit a voter to verify the ballot that she actually casts. Rather, it
+\term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
 allows users to verify a ballot without casting it (after which point it cannot be cast without
@@
 
-While both systems provide the voter some assurance that the proper vote was recorded, Scantegrity's
+While both systems provide the voter some assurance that the proper vote was recorded, \term{Scantegrity}'s
 verification process is more direct and provides a stronger guarantee that the ballot \emph{actually
@@
 
-In the case on Scantegrity, this information is primarily embodied in the published version of Table
+In the case on \term{Scantegrity}, this information is primarily embodied in the published version of Table
 Q. After the election, a voter can compare her receipt code with that revealed for his ballot in
@@
 
-Helios, similarly, exposes a complete list of ballot hashes. A voter can examine this data set to
+\term{Helios}, similarly, exposes a complete list of ballot hashes. A voter can examine this data set to
 ensure that it accurately reflects the hash that was reported on screen when the ballot was cast.
@@
 
-One source of vote auditing in Scantegrity relies on unused \term{audit ballots} to prove that its
+One source of vote auditing in \term{Scantegrity} relies on unused \term{audit ballots} to prove that its
 Tables Q, R, and S accurately match ballot selections with the proper candidates. These ballots come
@@
 
-In some ways, Helios count verification is simpler than that in Scantegrity. We have already
-discussed how Helios uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this
+In some ways, \term{Helios} count verification is simpler than that in \term{Scantegrity}. We have already
+discussed how \term{Helios} uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this
 mechanism, they are decrypted, and so the actual plaintext ballots are exposed. From that point,
@@
 
-Scantegrity prevents coercion via the manner it uses to encrypt ballots. Once cast, a ballot's
+\term{Scantegrity} prevents coercion via the manner it uses to encrypt ballots. Once cast, a ballot's
 ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
-without exposure of the data maintained in Table P -- Scantegrity's secret -- the voter has no
+without exposure of the data maintained in Table P -- \term{Scantegrity}'s secret -- the voter has no
 way to prove to a third party that the claim is true.
 
-An important point regarding Scantegrity is that it also relies on a \emph{physical property} -- the
+An important point regarding \term{Scantegrity} is that it also relies on a \emph{physical property} -- the
 invisible ink used when printing confirmation code bubbles -- to combat vote coercion (i.e., no
@@
 
-Helios, which is designed for use in an online setting, has no illusions about coercion: in fact,
+\term{Helios}, which is designed for use in an online setting, has no illusions about coercion: in fact,
 the public implementation makes it clear to voters that they would be easy to coerce. Setting
-physical security aside: as with Scantegrity, Helios does not reveal to a voter all the
+physical security aside: as with \term{Scantegrity}, \term{Helios} does not reveal to a voter all the
 information necessary to \emph{prove} a decryption of her ballot. Though a voter is able to see
@@
 
-The creators of Helios note this fact, and it is reflected in their work, as the system makes at
+The creators of \term{Helios} note this fact, and it is reflected in their work, as the system makes at
 least recording verification an obvious and easy process.
@@
 
-In both Scantegrity and Helios, the most fundamental secret is a key. In Scantegrity, this is the
-seed to the pseudorandom number generator used to create Table P; and in Helios, it is a single
+In both \term{Scantegrity} and \term{Helios}, the most fundamental secret is a key. In \term{Scantegrity}, this is the
+seed to the pseudorandom number generator used to create Table P; and in \term{Helios}, it is a single
 ElGamal key pair used for all encryption/decryption operations during a particular election.
 
-The random seed in Scantegrity is a secret that is shared among a group of members of the election
+The random seed in \term{Scantegrity} is a secret that is shared among a group of members of the election
 authority, thereby mitigating risk of compromise.
 
-But in Helios, there is a single private ElGamal key that lives on the server. The
-authors of Helios acknowledge this weakness but choose to overlook it, as they aim to make
+But in \term{Helios}, there is a single private ElGamal key that lives on the server. The
+authors of \term{Helios} acknowledge this weakness but choose to overlook it, as they aim to make
 verifiable voting an accessible technology, even with some costs.
@@
 in the body holding the election. This is the issue with secrets: \emph{someone} must keep them, and
-we must place some trust in that party. In Scantegrity, for example, we must assume that we can
+we must place some trust in that party. In \term{Scantegrity}, for example, we must assume that we can
 trust at least enough of the secret holders so that the seed cannot be obtained and used
@@
 
-It is clear that Scantegrity's secrets -- Tables P and R -- are generated using a source of true
+It is clear that \term{Scantegrity}'s secrets -- Tables P and R -- are generated using a source of true
 randomness. If there is any determinism in generating those tables, an attacker could exploit the
-generation method to violate privacy. Helios, on the other hand, was designed with application in
+generation method to violate privacy. \term{Helios}, on the other hand, was designed with application in
 mind and therefore uses standard cryptographic techniques (ElGamal and SHA-1).
 
-Given a flawless implementation of Scantegrity as specified in research, it can certainly provide the
+Given a flawless implementation of \term{Scantegrity} as specified in research, it can certainly provide the
 security it claims. However, we note that an amateur implementation of the protocol laid out by
-Scantegrity's creators -- e.g., one that uses a imperfect source of randomization -- could lead to a
+\term{Scantegrity}'s creators -- e.g., one that uses a imperfect source of randomization -- could lead to a
 very insecure system.
 
-The same can be said for Helios, should it be implemented with inappropriate primitives (not ElGamal
+The same can be said for \term{Helios}, should it be implemented with inappropriate primitives (not ElGamal
 and SHA-1); however, as the authors have designed the scheme with particular primitives in mind, its

### 2012-12-07 paper/paper.tex
Move period after citation.

@@
 A voter, or any other third party \term{auditor}, may also verify the accuracy of the final vote tallies
-reported by the election authority. \cite{preta}
+reported by the election authority \cite{preta}.
 Voting is complicated by the requirement that all votes remain secret to avoid coercion.

### 2012-12-07 paper/paper.tex
add preta mixing discussion

--- 2012-12-07 paper/paper.tex
@@
   existing voting procedures to provide fairness guarantees while maintaining ballot secrecy. We
-	detail security properties necessary to make an election both \term{verifiable} and \term{secret}
-	and analyze how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
+	detail security properties necessary to make an election both ``fair'' and ``secret'' and analyze
+	how three popular verifiable voting systems -- Scantegrity, \pv{}, and Helios --
 	use cryptographic techniques to meet those goals.
@@
 could be shown a screen giving the name of the candidate(s) she just voted for. If the display
-does not match the voter's intention, then the voter can try again -- or call into question the
+does not match the voter's intention, then the voter can ``try again'' -- or call into question the
 entire vote collection process.
@@
 Even in a receipt-free system,
-if the voting process involves a multi-step interaction involving the coercer,
+if the voting process involves a multi-step iteraction involving the coercer,
 it may be possible for the voter to prove to the coercer that she is following
@@
 Table S contains final vote tallies. Each column represents a particular candidate, and there will
-be one marked cell in each column for each ballot cast for that candidate.
+be one ``checked'' cell in each column for each ballot cast for that candidate.
 
@@
 All candidates are listed on the optical-scan ballot, and the voter makes her choice by filling
-in a bubble that reveals an alphanumeric confirmation code (as specified in the private Table
+in a ``bubble'' that reveals an alphanumeric confirmation code (as specified in the private Table
 P), which the voter then records on the receipt portion. The ballot is sent through an optical
@@
 
-Additionally, during the voting process, a voter can ask a poll worker for an second \term{audit}
+Additionally, during the voting process, a voter can ask a poll worker for an second ``audit''
 ballot. This ballot is initially just like any other ballot: however, \emph{all} candidate codes are
@@
 	\item
-		A check mark is placed on the row in Table R that maps the revealed Q value to some value in S.
+		A ``check'' is placed on the row in Table R that maps the revealed Q value to some value in S.
 	\item
-		The Table R mapping is followed into Table S, and a check mark is added to a cell in Table R,
+		The Table R mapping is followed into Table S, and a ``check'' is added to a cell in Table R,
 		to be counted as a vote for that row's candidate.
@@
 Once all votes have been cast and recorded, the election authority mixes, decrypts, and tallies the votes to determine the winners while maintaining ballot secrecy.
-Mixing the encrypted votes before or during the decryption process (depending on the \pv\ variant) ensures the votes remain anonymous, even to the officials performing the encryption, by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.
+Mixing the encrypted votes before or during the decryption process (depending on the \pv\ variant) ensures the votes remain anonymous -- even to the officials performing the encryption -- by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.
 
@@
 presented with a SHA-1 hash of her encrypted ballot. At this point, the voter may choose either
-to submit the ballot or to audit it. In the former case, the ballot is cast and voting is
-complete. But when a voter chooses to audit, she is presented with \emph{all} of the data
-used to encrypt the vote. Namely, this includes the public key and the randomness that were used
+to submit the ballot or to ``audit'' it. In the former case, the ballot is cast and voting is
+complete. But when a voter chooses to ``audit,'' she is presented with \emph{all} of the data
+used to encrypt the vote. Namely, this includes the public key and the ``randomness'' that were used
 by an implementation of ElGamal to encrypt the vote. The voter can then -- using a modified ElGamal
@@
 Once all ballots have been collected by the Helios server, they are shuffled by a cryptographic
-\term{mixnet}.
+``mixnet.''
 
@@
 
-The mixnet accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
+The ``mixnet'' accomplishes two goals: it shuffles the votes \emph{and} re-encrypts them (with the
 same key, but with different random inputs). A random permutation -- referred to as $\pi_{N}$ (where
 $N$ is the total number of votes) -- is first used to perform the shuffle. Each ciphertext
-$c_{i}$ is then \term{re-encrypted} to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
+$c_{i}$ is then ``re-encrypted'' to a new ciphertext $d_{i}$ that equivalent to the first \emph{had
 the random input at encrypt time been different} by a particular amount $s_{i}$. See Figure
@@
 
-The \term{shuffling} is important because it prevents an attacker from linking a decrypted ballot with
+The ``shuffling'' is important because it prevents an attacker from linking a decrypted ballot with
 a particular encrypted ballot -- and thus a voter. Re-encryption means that an auditor examining a
@@
 In order to provide a guarantee of proper shuffling, Helios shuffles the votes multiple
-times, actually using only the final shuffle in tallying the results. The other shuffles,
-referred to as ``shadow mixes'', are made public. Those mixes are hashed to obtain a bit string
+times, actually using only the final shuffle in tallying the results. The other shuffles are
+referred to as ``shadow mixes'' and are made public. Those mixes are hashed to obtain a bit string
 that is used, bit-for-bit, as a set of challenges, with one bit value indicating that Helios must
@@
 	\item
-		Mix the ballots in some way.
+		``Mix'' the ballots in some way.
 	\item
@@
 
-In Scantegrity, public version of a ballot is really just an encryption of the voter's
+In Scantegrity, ``public'' version of a ballot is really just an encryption of the voter's
 selections: it is an independent, uniformly random code chosen beforehand and corresponding to a
-particular candidate for that ballot. Table P defines an explicit, keyless encryption
+particular candidate for that ballot. Table P defines an explicit, ``keyless'' encryption
 function -- and each ballot holds just enough information from Table P to encrypt a single voter's
@@
 
-In Helios, the public ballot is a hash of an encryption. Helios uses ElGamal to encrypt ballots,
+In Helios, the ``public'' ballot is a hash of an encryption. Helios uses ElGamal to encrypt ballots,
 which -- unlike Scantegrity's core \emph{random} Table P -- could be subject to attack, given that
@@
 
-Essentially, both Scantegrity and Helios use some mechanism to shuffle votes so that -- even
+Essentially, each of these system uses some mechanism to ``shuffle'' votes so that -- even
 with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
@@
 
-In Scantegrity, the ballot mix is predetermined, as it is defined by the generation of Table R.
+In Scantegrity, the ballot ``mix'' is predetermined, as it is defined by the generation of Table R.
 When that table is constructed, ballots are pseudorandomly ordered. With the exception of audit
@@
 
-Where Table R lies between encryptions and decryptions in Scantegrity, Helios makes use of a
+Where Table R lies between encryptions and decryptions in Scantegrity, \pv\ and Helios make use of a
 cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
 tracing a vote to its decryption. Unlike in Scantegrity, \emph{all} encrypted votes can be traced to
-their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
-those one cannot connect those two traces, such that secrecy is preserved.
+their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally.
 
@@
 
-At the time a ballot is cast, both Scantegrity and Helios attempt to ensure a voter that her
+At the time a ballot is cast, these systems attempt to ensure a voter that her
 vote is recorded exactly as intended.
@@
 
-Helios does not actually permit a voter to verify the ballot that she actually casts. Rather, it
+\pv\ provides each voter with multiple ballots, one of which she actually casts, and the others
+she can audit to verify that the candidate permutation on the left-hand side corresponds to the one
+encoded in the onion on the right-hand side. Audited ballots cannot be cast, but since she chooses
+her actual ballot at random, if her audited ballots verify, she gains some confidence that
+her real ballot would as well. Auditing authorities also verify randomly selected ballots before,
+during, and after polling to garner further assurance.
+
+Like \pv, Helios does not actually permit a voter to verify the ballot that she actually casts. Rather, it
 allows users to verify a ballot without casting it (after which point it cannot be cast without
@@
 
-A common theme in verifiable voting systems seems to be the presence of a published \term{bulletin
-board} of votes. Note that because these boards contain only encrypted information, they do not
-violate ballot secrecy.
+A common theme in verifiable voting systems seems to be the presence of a published ``bulletin
+board'' of votes. (Note that because these boards contain only encrypted information, they do not
+violate ballot secrecy.)
 
@@
 \end{itemize}
-This technique -- verifying a random partial sample of the data -- is called \term{randomized partial
+This technique -- verifying a random partial sample of the data -- is called \term{random partial
 checking}. If these checks past, it is accepted that all other ballots must also be counted properly.
@@
 
-Scantegrity prevents coercion via the manner it uses to encrypt ballots. Once cast, a ballot's
+Scantegrity prevents coercion via the manner it uses to ``encrypt'' ballots. Once cast, a ballot's
 ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
-without exposure of the data maintained in Table P -- Scantegrity's secret -- the voter has no
+without exposure of the data maintained in Table P -- Scantegrity's ``secret'' -- the voter has no
 way to prove to a third party that the claim is true.
@@
 An important point regarding Scantegrity is that it also relies on a \emph{physical property} -- the
-invisible ink used when printing confirmation code bubbles -- to combat vote coercion (i.e., no
+invisible ink used when printing confirmation code ``bubbles'' -- to combat vote coercion (i.e., no
 one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
@@
 unlikely) that a crafty voter could fashion encryption details (a false key and false randomization
-data) that would produce the same hash but for a different candidate, thus convincing the coercer
-of something untrue.
-This is one reason that it is important for the system to use a collision-resistant hash function.
+data) that would produce the same hash but for a different candidate, thus ``proving'' something
+untrue to the coercing party. (This is one reason that it is important for the system to use a
+collision-resistant hash function.)
 
@@
 
-The public nature of this information can combat ballot stuffing. If names are associated with
+The public nature of this information can combat ``ballot stuffing.'' If names are associated with
 the posted ballots, then it should be obvious to one or more careful observers (given sufficient
 resources) that nonexistent persons are being posted. Furthermore, publication of ballots
-per-precinct can reveal stuffing should the number of ballots being reported by a particular
+per-precinct can reveal ``stuffing'' should the number of ballots being reported by a particular
 precinct/polling location be significantly higher than expected \cite{helios}.
@@
 One might wish to prevent a party from determining who did or did not cast \emph{any} ballot.
-As we've seen, \term{verifiable counting} typically relies on the public nature of this data.
-Additionally, should this data be hidden, it could potentially be more difficult to notice ballot
-stuffing.
+As we've seen, \term{verifiable counting} typically relies on the ``public'' nature of this data.
+Additionally, should this data be hidden, it could potentially be more difficult to notice ``ballot
+stuffing.''
 
@@
 tallied properly without \emph{anyone} being able to reveal the candidate selected on the ballot.
-Admittedly, to achieve this would be difficult: in the case of a single vote, tallying only that vote
+Admittedly, to achieve this would be difficult: in the case of a single vote, ``tallying'' just it
 would reveal the candidate for which it was cast. But if a secret \emph{must} be kept, it is

### 2012-12-07 paper/paper.tex

--- 2012-12-07 paper/paper.tex
@@
 
-Essentially, both \term{Scantegrity} and \term{Helios} use some mechanism to shuffle votes so that -- even
+Essentially, each of these system uses some mechanism to ``shuffle'' votes so that -- even
 with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext
@@
 
-Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{Helios} makes use of a
+Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \pv\ and \term{Helios} makes use of a
 cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
@@
 
-At the time a ballot is cast, both \term{Scantegrity} and \term{Helios} attempt to ensure a voter that her
+At the time a ballot is cast, these systems attempt to ensure a voter that her
 vote is recorded exactly as intended.
@@
 
-\term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
+\pv\ provides each voter with multiple ballots, one of which she actually casts, and the others
+she can audit to verify that the candidate permutation on the left-hand side corresponds to the one
+encoded in the onion on the right-hand side. Audited ballots cannot be cast, but since she chooses
+her actual ballot at random, if her audited ballots verify, she gains some confidence that
+her real ballot would as well. Auditing authorities also verify randomly selected ballots before,
+during, and after polling to garner further assurance.
+
+Like \pv, \term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
 allows users to verify a ballot without casting it (after which point it cannot be cast without

### 2012-12-07 paper/paper.tex
italicize more pretas

@@
 
-\pv\ \cite{preta} also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
+\term{\pv{}} \cite{preta} also aims to offer a familiar, in-person voting experience while providing cryptographic assurance of
 a fair election.
@@
 
-The paper ballot form in \pv\ consists of two separable sides.
+The paper ballot form in \term{\pv{}} consists of two separable sides.
 The left-hand side lists the candidates in permuted order.
@@
 Once all votes have been cast and recorded, the election authority mixes, decrypts, and tallies the votes to determine the winners while maintaining ballot secrecy.
-Mixing the encrypted votes before or during the decryption process (depending on the \pv\ variant) ensures the votes remain anonymous -- even to the officials performing the encryption -- by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.
+Mixing the encrypted votes before or during the decryption process (depending on the \term{\pv{}} variant) ensures the votes remain anonymous -- even to the officials performing the encryption -- by preventing discovery of any match between a particular encrypted vote and its decrypted counterpart.
 
-\pv\ accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
-\pv\ is flexible enough to use either a decryption or reencryption mixnet, and with the latter, a variety of encryption schemes.
-Scratch \& Vote \cite{scratch}, a variation on \pv, tallies the votes homomorphically rather than with a mixnet.
+\term{\pv{}} accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
+\term{\pv{}} is flexible enough to use either a decryption or reencryption mixnet, and with the latter, a variety of encryption schemes.
+Scratch \& Vote \cite{scratch}, a variation on \term{\pv}, tallies the votes homomorphically rather than with a mixnet.
 
@@
 
-Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \pv\ and \term{Helios} makes use of a
+Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{\pv{}} and \term{Helios} makes use of a
 cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
@@
 
-\pv\ provides each voter with multiple ballots, one of which she actually casts, and the others
+\term{\pv{}} provides each voter with multiple ballots, one of which she actually casts, and the others
 she can audit to verify that the candidate permutation on the left-hand side corresponds to the one
@@
 
-Like \pv, \term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
+Like \term{\pv{}}, \term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
 allows users to verify a ballot without casting it (after which point it cannot be cast without

### 2012-12-07 paper/paper.tex
remove unnecessary paragraphsentence
verifiable collection pret-a

@@
 
+\term{\pv{}} publishes the information on the right-hand side of each ballot, which mirrors the information contained on the corresponding voter's receipt.
+So, any voter who retains her receipt can verify that her vote was recorded exactly as cast.
+Moreover, if she discovers a mismatch, her signed receipt provides proof to that effect and can thus be used to call
+the election result into question.
+
 \term{Helios}, similarly, exposes a complete list of ballot hashes. A voter can examine this data set to

### 2012-12-07 paper/paper.tex
pv

@@
 
-It is important that we have considered secrecy mechanisms first, as these strategies enable
-fulfillment of other goals, such as \emph{verifiability}.
-
 \subsection{Verifiable recording}
@@
 
-The same can be said for \term{Helios}, should it be implemented with inappropriate primitives (not ElGamal
-and SHA-1); however, as the authors have designed the scheme with particular primitives in mind, its
-specification is less open to interpretation and, therefore, potentially harmful choices.
+The same can be said for \term{\pv{}} and \term{Helios}, should they be implemented with inappropriate primitives; however, as the authors have designed the schemes with particular primitives in mind, their
+specifications are less open to interpretation and, therefore, potentially harmful choices.
 

### 2012-12-07 paper/paper.tex
Discuss verifiability of counting in PV

@@
 \term{\pv{}} accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
-\term{\pv{}} is flexible enough to use either a decryption or reencryption mixnet, and with the latter, a variety of encryption schemes.
+\term{\pv{}} is flexible enough to use either a decryption or re-encryption mixnet, and with the latter, a variety of encryption schemes.
 Scratch \& Vote \cite{scratch}, a variation on \term{\pv}, tallies the votes homomorphically rather than with a mixnet.
@@
 
-In order to provide a guarantee of proper shuffling, \term{Helios} shuffles the votes multiple
-times, actually using only the final shuffle in tallying the results. The other shuffles,
-referred to as ``shadow mixes'', are made public. Those mixes are hashed to obtain a bit string
-that is used, bit-for-bit, as a set of challenges, with one bit value indicating that \term{Helios} must
-provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
-other bit value indicating that it must provide a mapping from one shadow mix to another. This is
-known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
-obtain the set of challenges allows this process to be completed entirely within the \term{Helios} system
--- without human involvement -- for publication and auditor verification.
-
-Once auditors are satisfied with the proofs, \term{Helios} decrypts and tallies the ballots. Similarly,
-\term{Helios} proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
+Auditors are then provided with proofs for verification of proper mixing (see later analysis). Once
+auditors are satisfied, \term{Helios} decrypts and tallies the ballots. Similarly, \term{Helios}
+proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
 known as the \term{Chaum-Pedersen protocol}, through which the system proves that \emph{all}
@@
 
+\term{Helios} must prove to auditors that ballots have been properly mixed. To do so, \term{Helios}
+shuffles the votes multiple times, actually using only the final shuffle in tallying the results.
+The other shuffles, referred to as ``shadow mixes'', are made public. Those mixes are hashed to
+obtain a bit string that is used, bit-for-bit, as a set of challenges, with one bit value indicating
+that \term{Helios} must provide the permutation used for the shuffle and the $s_{i}$ values used for
+re-encryption, and the other bit value indicating that it must provide a mapping from one shadow mix
+to another. This is known as a challenge-response \term{Honest-Verifier Zero-Knowledge} proof, and the
+use of a hash to obtain the set of challenges allows this process to be completed entirely within
+the \term{Helios} system -- without human involvement -- for publication and auditor verification.
+
 In some ways, \term{Helios} count verification is simpler than that in \term{Scantegrity}. We have already
@@
 mechanism, they are decrypted, and so the actual plaintext ballots are exposed. From that point,
-tallying is straightforward.
+tallying is straightforward and trivially-verifiable via simple arithmetic.
+
+\term{\pv{}} provides for verification of counting using techniques seen in both \term{Scantegrity}
+and \term{Helios}: a mixnet proof based on randomized partial checking in which a random selection
+determines points in the mixnet for which a mix server must show how it has mixed a particular vote.
+Though it is not permitted for this selection to trace any one vote throughout the mixnet in order
+to preserve privacy, it provides sufficient proof that the overall mixnet has shuffled votes
+accurately.
+
+As with \term{Helios}, votes are decrypted after exiting the mixnet and can tallied in a
+trivially-verifiable manner.
 

### 2012-12-08 paper/paper.tex
Move a paragraph in the introduction
Correct terminology

@@
 
+An election involves an information exchange between many independent \term{voters} and a single
+\term{election authority}.
+In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
+by the election authority.
+A voter, or any other third party \term{auditor}, may also verify the accuracy of the final vote tallies
+reported by the election authority \cite{preta}.
+Voting is complicated by the requirement that all votes remain secret to avoid coercion.
+
 In this survey, we study three of the most well-known solutions: the in-person voting systems
@@
 we draw conclusions about the role of these schemes in elections today and in the future.
-
-An election involves an information exchange between many independent \term{voters} and a single
-\term{election authority}.
-In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
-by the election authority.
-A voter, or any other third party \term{auditor}, may also verify the accuracy of the final vote tallies
-reported by the election authority \cite{preta}.
-Voting is complicated by the requirement that all votes remain secret to avoid coercion.
 
@@
 
-Once votes have been collected, it is the responsibility of the state to tally votes for the various
+Once votes have been collected, it is the responsibility of the election authority to tally votes for the various
 candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on

### 2012-12-08 paper/paper.tex
Remove inaccurate sentence

@@
 
-These systems, however, allow publication of data sufficient to verify tallies. Relying on
-cryptography to ensure secrecy, each system involves exposure of cryptographically-hidden vote
-counts that can be used to ensure that -- given all votes cast -- the final tallies are correct.
+These systems, however, allow publication of data sufficient to verify tallies while relying on
+cryptography to ensure secrecy.
 

### 2012-12-08 paper/paper.tex
Remove quotation marks

@@
 
-Essentially, each of these system uses some mechanism to ``shuffle'' votes so that -- even
+Essentially, each of these system uses some mechanism to shuffle votes so that -- even
 with votes decrypted for tallying -- encrypted ballots cannot be linked to their plaintext

### 2012-12-08 paper/paper.tex
pret-a

--- 2012-12-08 paper/paper.tex
@@
 
-An election involves an information exchange between many independent \term{voters} and a single
-\term{election authority}.
-In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
-by the election authority.
-A voter, or any other third party \term{auditor}, may also verify the accuracy of the final vote tallies
-reported by the election authority \cite{preta}.
-Voting is complicated by the requirement that all votes remain secret to avoid coercion.
-
 In this survey, we study three of the most well-known solutions: the in-person voting systems
@@
 we draw conclusions about the role of these schemes in elections today and in the future.
+
+An election involves an information exchange between many independent \term{voters} and a single
+\term{election authority}.
+In a \term{verifiable} election, each voter may verify that her own vote was counted correctly
+by the election authority.
+A voter, or any other third party \term{auditor}, may also verify the accuracy of the final vote tallies
+reported by the election authority \cite{preta}.
+Voting is complicated by the requirement that all votes remain secret to avoid coercion.
 
@@
 
-Once votes have been collected, it is the responsibility of the election authority to tally votes for the various
+Once votes have been collected, it is the responsibility of the state to tally votes for the various
 candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
@@
 \term{\pv{}} accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
-\term{\pv{}} is flexible enough to use either a decryption or re-encryption mixnet, and with the latter, a variety of encryption schemes.
+\term{\pv{}} is flexible enough to use either a decryption or reencryption mixnet, and with the latter, a variety of encryption schemes.
 Scratch \& Vote \cite{scratch}, a variation on \term{\pv}, tallies the votes homomorphically rather than with a mixnet.
@@
 
-Auditors are then provided with proofs for verification of proper mixing (see later analysis). Once
-auditors are satisfied, \term{Helios} decrypts and tallies the ballots. Similarly, \term{Helios}
-proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
+In order to provide a guarantee of proper shuffling, \term{Helios} shuffles the votes multiple
+times, actually using only the final shuffle in tallying the results. The other shuffles,
+referred to as ``shadow mixes'', are made public. Those mixes are hashed to obtain a bit string
+that is used, bit-for-bit, as a set of challenges, with one bit value indicating that \term{Helios} must
+provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
+other bit value indicating that it must provide a mapping from one shadow mix to another. This is
+known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
+obtain the set of challenges allows this process to be completed entirely within the \term{Helios} system
+-- without human involvement -- for publication and auditor verification.
+
+Once auditors are satisfied with the proofs, \term{Helios} decrypts and tallies the ballots. Similarly,
+\term{Helios} proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
 known as the \term{Chaum-Pedersen protocol}, through which the system proves that \emph{all}
@@
 
-In both \term{Scantegrity} and \term{Helios}, the following information is revealed after the election:
+In all three systems, the following information is revealed after the election:
 \begin{itemize}
@@
 
-Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{\pv{}} and \term{Helios} makes use of a
+Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{\pv{}} and \term{Helios} make use of a
 cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
@@
 
-\term{Helios} must prove to auditors that ballots have been properly mixed. To do so, \term{Helios}
-shuffles the votes multiple times, actually using only the final shuffle in tallying the results.
-The other shuffles, referred to as ``shadow mixes'', are made public. Those mixes are hashed to
-obtain a bit string that is used, bit-for-bit, as a set of challenges, with one bit value indicating
-that \term{Helios} must provide the permutation used for the shuffle and the $s_{i}$ values used for
-re-encryption, and the other bit value indicating that it must provide a mapping from one shadow mix
-to another. This is known as a challenge-response \term{Honest-Verifier Zero-Knowledge} proof, and the
-use of a hash to obtain the set of challenges allows this process to be completed entirely within
-the \term{Helios} system -- without human involvement -- for publication and auditor verification.
-
 In some ways, \term{Helios} count verification is simpler than that in \term{Scantegrity}. We have already
@@
 mechanism, they are decrypted, and so the actual plaintext ballots are exposed. From that point,
-tallying is straightforward and trivially-verifiable via simple arithmetic.
-
-\term{\pv{}} provides for verification of counting using techniques seen in both \term{Scantegrity}
-and \term{Helios}: a mixnet proof based on randomized partial checking in which a random selection
-determines points in the mixnet for which a mix server must show how it has mixed a particular vote.
-Though it is not permitted for this selection to trace any one vote throughout the mixnet in order
-to preserve privacy, it provides sufficient proof that the overall mixnet has shuffled votes
-accurately.
-
-As with \term{Helios}, votes are decrypted after exiting the mixnet and can tallied in a
-trivially-verifiable manner.
+tallying is straightforward.
 
@@
 
+In \term{\pv{}}, the secrets are the layered permutations of the candidate list corresponding to each ballot as encoded in its onion.
+During the tallying phase, the end-to-end mapping from encrypted to decrypted ballot must also be concealed from any single party.
+
 In both \term{Scantegrity} and \term{Helios}, the most fundamental secret is a key. In \term{Scantegrity}, this is the

### 2012-12-08 paper/paper.tex
Add missing article

@@
 
-In \term{Scantegrity}, public version of a ballot is really just an encryption of the voter's
+In \term{Scantegrity}, the public version of a ballot is really just an encryption of the voter's
 selections: it is an independent, uniformly random code chosen beforehand and corresponding to a

### 2012-12-08 paper/paper.tex
Discuss ballot encryption in PV

@@
 ballot number is the key. However, the table is a collection of \emph{all the keys}, and its
-compromise would eliminate ballot secrecy for all ballots.)
+compromise would eliminate ballot secrecy for all ballots.) But it is important to note that this
+table can be reconstructed using the same pseudorandom number generator as during initial creation
+along with the (shared secret) generator seed.
 
@@
 security: rather, we simply note that the difference between these two systems can be thought of as
-a tradeoff between key size and privacy guarantees. \term{Scantegrity} essentially has an immensely large
-key that -- because it is theoretically completely random -- ensures that ciphertext cannot be
-decrypted. \term{Helios}, however, uses known algorithms with shorter keys that could potentially be
-attacked. Compromise of keys in either system would destroy their privacy guarantees.
+a tradeoff between key size and privacy guarantees.
+
+With \term{\pv{}}, the submitted ballot is really just a position within a permutation of the
+candidates. The \emph{position} within the permutation is not encrypted: rather, the candidate
+permutation is secret and can be obtained (later in the election process) from the onion.
+
+Considering the confirmation codes from a ballot, \term{Scantegrity} seems to have an immensely
+large key that -- because it is theoretically random -- ensures that ciphertext cannot be decrypted.
+But compromise of the much shorter generator seed could be used to obtain the same information.
+\term{Helios} and \term{\pv{}} more simply use known algorithms with secret keys. Key compromise
+would destroy the privacy guarantees of any of these systems.
 

### 2012-12-08 paper/paper.tex
Fix repetition of "actually"
pret-a vis-a-vis coercion resistance

--- 2012-12-08 paper/paper.tex
@@
 
+\term{\pv{}} acknowledges that it generally only provides receipt-freeness and thus voter privacy, but fails to
+truly resist coercion. It offers receipt-freeness, despite providing voters with a receipt, because a voter
+cannot use her receipt to prove for whom she voted. Absent perfect physical security, though, coercion may still be possible
+by, for example, sneaking complete, blank ballot forms out of the polling place, recording the candidate list ordering and onion on each,
+giving the forms to other voters to sneak in and use to vote, and then requiring those voters to show that their signed receipt, matched with the now-known candidate ordering, indicates they voted as instructed.
+
 \term{Helios}, which is designed for use in an online setting, has no illusions about coercion: in fact,

### 2012-12-08 paper/paper.tex

--- 2012-12-08 paper/paper.tex
@@
 
-Like \term{\pv{}}, \term{Helios} does not actually permit a voter to verify the ballot that she actually casts. Rather, it
+Like \term{\pv{}}, \term{Helios} does not permit a voter to verify the ballot that she actually casts. Rather, it
 allows users to verify a ballot without casting it (after which point it cannot be cast without

### 2012-12-08 paper/paper.tex
Make some small fixes

@@
 to hash encrypted ballots. Note that we are not making a precise quantification about \term{Helios}'s
-security: rather, we simply note that the difference between these two systems can be thought of as
+security. Rather, we simply note that the difference between these two systems can be thought of as
 a tradeoff between key size and privacy guarantees.
 
-With \term{\pv{}}, the submitted ballot is really just a position within a permutation of the
-candidates. The \emph{position} within the permutation is not encrypted: rather, the candidate
-permutation is secret and can be obtained (later in the election process) from the onion.
+With \term{\pv{}}, the submitted ballot is the selected candidate's position within a permutation of
+the candidates. The \emph{position} within the permutation is not encrypted; rather, the permutation
+itself is secret and can be obtained (later in the election process) from the onion.
 

### 2012-12-08 paper/paper.tex
Work on analysis of ballot secrecy

@@
 \subsection{After voting}
-A publicly-available bulletin board publishes all recorded votes, i.e., the right-hand sides of each cast ballot, including its onion and vote as recorded.
+A publicly-available bulletin board publishes all recorded votes, i.e., the right-hand side of each cast ballot, including its onion and vote as recorded.
 A voter can then verify that her vote was correctly recorded by checking that her receipt matches the information displayed on the bulletin board.
@@
 Scratch \& Vote \cite{scratch}, a variation on \term{\pv}, tallies the votes homomorphically rather than with a mixnet.
+
+Voters must rely on varied auditing authorities to verify this tallying process.
 
@@
 
-\subsection{Coercion prevention}
+\subsection{Ballot secrecy}
 
-\term{Scantegrity} prevents coercion via the manner it uses to encrypt ballots. Once cast, a ballot's
-ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
-without exposure of the data maintained in Table P -- \term{Scantegrity}'s secret -- the voter has no
-way to prove to a third party that the claim is true.
+\term{Scantegrity} resists coercion via the manner it uses to encrypt ballots. Firstly, assuming
+physical security, without access to Table P or Table R, one cannot predict the confirmation codes
+that will be produced by casting a ballot in a particular manner. Secondly, without exposure of the
+data maintained in Table P or Table R, a voter has no way to prove to a third party that she has
+voted as claimed.
 
 An important point regarding \term{Scantegrity} is that it also relies on a \emph{physical property} -- the
-invisible ink used when printing confirmation code bubbles -- to combat vote coercion (i.e., no
-one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
-the person for having voted a certain way). This is akin to keeping Table P a secret: the ballots
-together \emph{are} Table P, and using special ink allows the codes to be printed without making it
-easy for a ballot handler to simple read Table P from the ballots prior to the election.
+invisible ink used when printing confirmation code bubbles -- to combat vote coercion. This is akin
+to keeping Table P a secret: the ballots together \emph{are} Table P, and using special ink allows
+the codes to be printed without making it easy for a ballot handler to simple read Table P from the
+ballots prior to the election.
 

### 2012-12-08 paper/paper.tex
Mention receipt-freeness

--- 2012-12-08 paper/paper.tex
@@
 the public implementation makes it clear to voters that they would be easy to coerce. Setting
-physical security aside: as with \term{Scantegrity}, \term{Helios} does not reveal to a voter all the
-information necessary to \emph{prove} a decryption of her ballot. Though a voter is able to see
+physical security aside, as with \term{Scantegrity}, \term{Helios} does not reveal to a voter all the
+information necessary to \emph{prove} a decryption of her ballot, thus providing receipt-freeness. Though a voter is able to see
 encryption details for ballots chosen for audit, that information is never displayed to the user

### 2012-12-08 paper/paper.tex
Mention PV in discussion

@@
 and a second to Table S, and neither of these can be compromised to ensure secrecy for all ballots.
-But in \term{Helios}, use of a cryptographic mixnet means that both inputs and outputs can be mapped to
-voters and tallies, respectively, without revealing the inner mapping. In some ways, \term{Helios}'s
-approach accomplishes the same goals as \emph{but} is implemented as an antithesis of \term{Scantegrity}'s
-Table system.
+But in \term{\pv{}} and \term{Helios}, use of a cryptographic mixnet means that both inputs and outputs can be mapped to
+voters and tallies, respectively, without revealing the inner mapping. While accomplishing the same
+goals as \term{Scantegrity}'s Table system, this approach is in some ways its antithesis.
 

### 2012-12-08 paper/paper.tex
pret-a

--- 2012-12-08 paper/paper.tex
@@
 
-While both systems provide the voter some assurance that the proper vote was recorded, \term{Scantegrity}'s
+While each system provides the voter some assurance that the proper vote was recorded, \term{Scantegrity}'s
 verification process is more direct and provides a stronger guarantee that the ballot \emph{actually
